---
title: "Basic Needs Programs and Services"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
source("common_code.R")
page.num <- 6
```

The following questions were asked in regards to the participation and impact of Basic Needs programs and services on students lives. Students were asked to evaluate how they feel these programs have benefited them both academically and non-academically, as well as barriers/reasons in regards to why they are not using certain programs. This includes programs such as CalFresh, Food Pantries, Meal Programs, Medi-Cal (also known as Medi-Cade in the United States), and Emergency Housing Services. 

# Participation
**Pick all Basic Needs Programs and Services that you participate in (mark all that apply):**
```{r, fig.width=8.5}
questions <- bns %>% select(starts_with("q46_"))

questions <- questions %>% mutate(across(everything(), function(x) fct_relevel(x, "Never heard of it", "Heard of it, but never used it",
                                                                               "Used it before attending college", 
                                                                               "Used it in the past as a college student",
                                                                               "Currently use as a college student")))

names(questions) <- c('CalFresh (also known as Food Stamps or SNAP benefits)',
                      'Campus food pantry (e.g., food, toiletries, feminine products)',
                      'Restaurant Meals Program (ability to use CalFresh EBT for hot meals on campus)',
                      'MediCal',
                      'Emergency Housing Services')
plot_likert(questions,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
`r fig.cap(page.num, "Participation in Basic Needs Programs")`

# Impact

## CalFresh EBT
*Note: for the first graph on EBT application we have `r print_n_reporting("q47")` And for the second graph on how many people are fed we have `r print_n_reporting("fed_through_EBT")`*
```{r, fig.width=8.5}
p1 <- plot_frq(bns$q47, wrap.title = 40, ylim=c(0,125), wrap.labels = 15, 
               title="Did you apply for CalFresh EBT as an individual or with other people in your household?") +
  xlab('')
p2 <- plot_frq(bns$fed_through_EBT, wrap.title = 40, title="How many people in the household are regularly fed through your CalFresh EBT card?") + xlab('')

grid.arrange(p1, p2, nrow=1)
rm(p1,p2)
```
`r fig.cap(page.num, "CalFresh EBT: Application & Feeding")`

Looking at the above graphs, the majority of people apply for CalFresh EBT as an individual (`r unname(table(bns$q47)['As an individual'])` people) while only `r unname(table(bns$q47)['With other people in my household'])` people applied with other people in their household. Similarly, the majority of people claimed only `r names(sort(table(bns$fed_through_EBT), decreasing = TRUE))[1]` person is fed through the EBT card (`r unname(sort(table(bns$fed_through_EBT), decreasing = TRUE))[1]` people). `r unname(sort(table(bns$fed_through_EBT), decreasing = TRUE))[2]` people claim to feed `r names(sort(table(bns$fed_through_EBT), decreasing = TRUE))[2]` people through the EBT card, and only a small amount of people claim to feed 5 or more people through the EBT card.

### Monthly CalFresh Money
**How much money do you receive from CalFresh each month? `r print_n_reporting("q49_1")`**
```{r, fig.width=7}
hist_with_box('q49_1', 29, 3, 0.2, NULL, c(0,32), 'Monthly Support ($)')
```
`r fig.cap(page.num, "Monthly Allowance from CalFresh")`

The average amount of money received for people using CalFresh (denoted by the dotted line) is \$`r round(mean(bns$q49_1, na.rm=TRUE),2)`, while the median is \$`r round(median(bns$q49_1, na.rm=TRUE),2)`. The values range from \$`r min(bns$q49_1, na.rm=TRUE)` to \$`r max(bns$q49_1, na.rm=TRUE)`. The majority of people who do receive these benefits seems to be getting around \$250 or less per month.

### Is This Enough?
*Note: for the first graph on if the allowance is enough we have `r print_n_reporting("q50")` And for the second graph on when people run out we have `r print_n_reporting("q51")`*
```{r, fig.height=4.5, fig.width=8.5}
p1 <- plot_frq(bns$q50, ylim=c(0,125), title="Do you feel that this is enough money to provide healthy food for the month?") + xlab('')
p2 <- plot_frq(bns$q51, wrap.labels = 12, title="If \"No\", then when do you typically run out?") + xlab('')

grid.arrange(p1, p2, nrow=1)
rm(p1,p2)
```
`r fig.cap(page.num, "Enough Monthly Allowance and Time of Exhaustion")`

Of the people who do receive money from CalFresh, `r unname(table(bns$q50)['Yes'])` of them claim that it is enough money to provide healthy food for a month and `r unname(table(bns$q50)['No'])` of them feel that it is not enough. People who do not feel it is enough money typically run out of CalFresh money in either the second week (`r unname(table(bns$q51)['Second week after receiving benefits'])` people) or third week (`r unname(table(bns$q51)['Third week after receiving benefits'])` people). A small group also run out within the first week, while an even smaller minority run out in the fourth week.

## CalFresh Benefits
**While you received CalFresh benefits:**
```{r, fig.height=8, fig.width=8.5}
questions <- bns %>% select(starts_with("q52_"))
names(questions) <- c('I worked fewer hours each week in a PAID position.',
                      'I had more time to do an UNPAID internship or volunteer work.',
                      'I had more money to pay for bills (rent, utility bills, clothes, etc.).',
                      'I had more money for entertainment and social activities.',
                      'I shopped more frequently at the farmers market.',
                      'I had learned more about healthier foods.',
                      'I purchased healthier foods.',
                      'I cooked more frequently at home.',
                      'I consumed a healthier diet.',
                      'I consumed less fast food.',
                      'I consumed fewer processed foods.',
                      'I consumed fewer sugar-sweetened beverages like soda and energy drinks.',
                      'I consumed less alcohol or fewer alcoholic beverages.',
                      'I concentrated more in class(es).',
                      'My grades had improved.',
                      'My grades had decreased.',
                      'I kept up with course materials..',
                      'I had more time to go to my professors office hours and tutoring services when needed.',
                      'I had more time to attend all classes as they are scheduled.',
                      'I had more time to go on field trips or internships.',
                      'My sleep quality had improved.',
                      'My stress/anxiety level had decreased.')
plot_likert(questions[1:11],
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")

plot_likert(questions[11:22],
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
`r fig.cap(page.num, "Perceived Benefits of CalFresh")`

## CalFresh Barriers
**What are the reasons you do not have CalFresh or have never used CalFresh? (Select all that apply).**
```{r}
question <- "barrier"
qlabel <- c('I do not think I’m eligible ',
            'I have heard from other students that it’s not worth my time because I won’t be eligible or I won’t receive much money.',
            'I am embarrassed or ashamed to apply for CalFresh.',
            'My family or household does not want to apply for CalFresh.',
            "I don't need CalFresh.",
            'I feel other students need CalFresh more than I do.',
            'No time to complete the application/ application is too long.',
            'No time to get verification documents or don’t know how to get verification document.',
            'No time to call or go to the local social service office for my CalFresh interview.',
            'I don’t believe in social services like CalFresh, WIC, or Welfare',
            'No transportation',
            'Other',
            'The application is too difficult.',
            'The CalFresh outreach team on campus was not helpful or supportive during my application process.',
            'The staff in my local county social service office were not helpful or supportive during my application process.')

cf_barrier_vars <- prep_binary_vars(question, qlabel)

# Plot table of Percentages
cf_barrier_vars %>% 
  select(Measure = xlab, "Yes (%)" = pct_lab) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped")
```

## Campus Food Pantry
**For the following questions, please choose how much you agree or disagree with the impact campus food pantries has or had on your life. While I utilized campus food pantry/pantries:**
```{r, fig.height=8, fig.width=8.5}
questions <- bns %>% select(starts_with("q55_"))
names(questions) <- c('I worked fewer hours each week in a PAID position.',
                      'I had more time to do an UNPAID internship or volunteer work.',
                      'I had more money to pay for bills (rent, utility bills, clothes, etc.).',
                      'I had more money for entertainment and social activities.',
                      'I shopped more frequently at the farmers market.',
                      'I had learned more about healthier foods.',
                      'I purchased healthier foods.',
                      'I cooked more frequently at home.',
                      'I consumed a healthier diet.',
                      'I consumed less fast food.',
                      'I consumed fewer processed foods.',
                      'I consumed fewer sugar-sweetened beverages like soda and energy drinks.',
                      'I consumed less alcohol or fewer alcoholic beverages.',
                      'I concentrated more in class(es).',
                      'My grades had improved.',
                      'My grades had decreased.',
                      'I kept up with course materials.',
                      'I had more time to go to my professors office hours and tutoring services when needed.',
                      'I had more time to attend all classes as they are scheduled.',
                      'I had more time to go on field trips or internships.',
                      'My sleep quality had improved.',
                      'My stress/anxiety level had decreased.')
plot_likert(questions[1:11],
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")

plot_likert(questions[11:22],
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
`r fig.cap(page.num, "Perceived Impact of Campus Food Pantry")`

### Food Pantry Use
**How often do you normally use the food pantry or if you are not currently using it, how often did you use it? `r print_n_reporting("q54")`**
```{r}
plot_frq(bns$q54, wrap.labels = 15) + xlab('Food Pantry Use Frequency')
```
`r fig.cap(page.num, "Food Pantry Use Frequency")`

When people use the food pantry, the majority do not use it every week (`r unname(sort(table(bns$q54), decreasing = TRUE)['Not every week'])` people). `r unname(sort(table(bns$q54), decreasing = TRUE)['About once a week'])` people claim to use it about once a week, `r unname(sort(table(bns$q54), decreasing = TRUE)['More than once a week'])` people use it more than once a week, and `r unname(sort(table(bns$q54), decreasing = TRUE)['Other'])` people claim other uses.

### Reasons Not Using Food Pantries
**What are the reasons for you to not go to campus food pantries? (Select all that apply).**
```{r}
question <- "no_pantry"
qlabel <- c("My family doesn't want me to go to campus food pantries or local food banks.",
            'I am embarrassed or scared to go to the campus food pantries or local food banks.',
            'I do not believe in using campus food pantries or local food banks.',
            "Inconvenient to access due to lack of transportation or out-of-the way location.",
            'Inconvenient times of operation/limited pantry hours.',
            'I feel other students need the food more than I do.',
            'I am not aware of any campus food pantries or local food banks.',
            'There are no food pantries close to campus or my residence',
            'Other')

pantry_vars <- prep_binary_vars(question, qlabel)

# Plot table of Percentages
pantry_vars %>% 
  select(Measure = xlab, "Yes (%)" = pct_lab) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped")
```

## Restaurant Meal Program (RMP)
**While you participated in the Restaurant Meal Program (RMP):**
```{r, fig.height=8.5, fig.width=8.5}
questions <- bns %>% select(starts_with("q57_"))
names(questions) <- c('I have more time to receive assistance from the Accessibility Resource Center (ARC) or other disability programs.',
                      'I concentrated more in class(es).',
                      'My grades had improved.',
                      'My grades had decreased.',
                      'I kept up course materials.',
                      'I had more time to go to my professors’ office hours and tutoring services when needed.',
                      'I had more time to attend all classes as they are scheduled.',
                      'I had more time to go on field trips or internships.',
                      'My sleep quality had improved.',
                      'My stress/anxiety level had decreased..',
                      'I’m less concerned about housing issues.',
                      'I felt more confident in my ability to maintain healthy relationships.')

plot_likert(questions,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
`r fig.cap(page.num, "Perceived Impact of Restaurant Meal Program (RMP)")`

### Reasons Not Using RMP
**What are the reasons for you to not have RMP or have never used RMP? (Select all that apply).**
```{r}
question <- "RMP"
qlabel <- c("I don’t need this Restaurant Meal Program (RMP).",
            'I have no access to these participating restaurants/no convenient locations.',
            'I have no transporation to these restaurants.',
            'I have no time to go to these restaurants.',
            'I have never heard about this Restaurant Meal Program (RMP).',
            'I am emberarrassed or ashamed to use my EBT card in a restaurant.',
            'I do not like the food offered in these participating restaurants.',
            "I don’t believe in social services like RMP, Medi-Cal, CalFresh, WIC, or Welfare/Cash Aid.",
            'Other')

rmp_vars <- prep_binary_vars(question, qlabel)

# Plot table of Percentages
rmp_vars %>% 
  select(Measure = xlab, "Yes (%)" = pct_lab) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped")
```

## Medi-Cal
**Knowing that you have Medi-Cal:**
```{r, fig.width=8.5}
questions <- bns %>% select(starts_with("q59_"), "q60")
names(questions) <- c("My mental health has improved.",
                      "My physical health has improved.",
                      "My sleep quality had improved.",
                      "My stress/anxiety level had decreased.",
                      "I was able to receive the healthcare I needed")

plot_likert(questions,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
`r fig.cap(page.num, "Perceived Impact of Medi-Cal")`

### Reasons Not Using Medi-Cal
**What are the reasons you do not have Medi-Cal or have never used Medi-Cal? (Select all that apply).**
```{r}
question <- "no_medical"
qlabel <- c("I don’t need MediCal.",
            "I do not know what MediCal is or I think I already have health insurance.",
            "I only need medical services at the student health center associated with my campus.",
            "No time to complete the MediCal application/MediCal application is too long.",
            "The MediCal application is too difficult to complete.",
            "I do not think I am eligible for MediCal.",
            "I have heard from other students that it is not worth my time because I wont be eligible.",
            "My family or household does not want me to apply for MediCal.",
            "I am embarrassed or ashamed to apply for MediCal.",
            "I don’t believe in social services like MediCal, CalFresh, WIC, or Welfare/Cash Aid.",
            "Other")

medical_vars <- prep_binary_vars(question, qlabel)

# Plot table of Percentages
medical_vars %>% 
  select(Measure = xlab, "Yes (%)" = pct_lab) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped")
```

## Emergency Housing Services (EHS)
```{r, fig.height=7.5, fig.width=8.5}
questions <- bns %>% select(starts_with("q62_"))
names(questions) <- c('I concentrated more in class(es).',
                      'My grades had improved.',
                      'My grades had decreased.',
                      'I kept up course materials.',
                      'I had more time to go to my professors’ office hours and tutoring services when needed.',
                      'I had more time to attend all classes as they are scheduled.',
                      'I had more time to go on field trips or internships.',
                      'My sleep quality had improved.',
                      'My stress/anxiety level had decreased.',
                      'I’m less concerned about housing issues.',
                      'I felt more confident in my ability to maintain healthy relationships.')

plot_likert(questions,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
`r fig.cap(page.num, "Perceived Impact of Emergency Housing Services (EHS)")`

### Reasons Not Using EHS
**What are the reasons you do not have Emergency Housing Services or have never used Emergency Housing Services?**
```{r}
question <- "EHS"
qlabel <- c("I don’t need Emergency Housing Services",
            "I was not aware that my campus had Emergency Housing Services like grants and housing placements in an emergency.",
            "No time to complete the Emergency Housing application or contact the Emergency Housing Staff.",
            "The Emergency Housing Services application is too difficult to complete.",
            "The emergency housing grant/money is not enough to support what I need, so not worth my time to apply for it.",
            "I am embarrassed or ashamed to apply for Emergency Housing Services.",
            "I do not believe in social services like Emergency Housing Services, MediCal, CalFresh, or Welfare/Cash Aid.",
            "Other")

ehs_vars <- prep_binary_vars(question, qlabel)

# Plot table of Percentages
ehs_vars %>% 
  select(Measure = xlab, "Yes (%)" = pct_lab) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped") %>% column_spec(2, width='3.5cm')
```
