---
title: "Workload by Campus"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
source("common_code.R")
```
The following is a comparison across the 3 campuses (Chico, Fresno, and Northridge) for information relating to the workload taken on by students, both academic and non-academic.

## Paid Hours Per Week
```{r, fig.height=4.6, fig.width=7.6}
bns$paid_work_hours <- fct_relevel(factor(bns$paid_work_hours), "0", "1-5", "6-10")

plot_grpfrq(bns$paid_work_hours, bns$school, wrap.legend.labels = 30, geom.colors = campus.colors, legend.title = "", show.prc = FALSE) + 
  xlab('') + theme(legend.position="top")
```


## Unpaid Hours Per Week
```{r, fig.height=4.6, fig.width=8}
bns$unpaid_work_hours <- fct_relevel(factor(bns$unpaid_work_hours), "0", "1-5", "6-10")

plot_grpfrq(bns$unpaid_work_hours, bns$school, wrap.legend.labels = 30, geom.colors = campus.colors, legend.title = "", show.prc = FALSE) + 
  xlab('') + theme(legend.position="top")
```


## Academic Hours
```{r, fig.height=8, fig.width=7}
tmp <- data.frame(q18=bns$q18, school=bns$school) %>% mutate(q18=recode(q18, "22+"="22"), q18=as.numeric(q18),
                                                             units=q18*3) %>% select(-q18)

ggplot(data=tmp, aes(x=units, fill=school)) + geom_histogram() + facet_wrap(~school, dir="v") + xlab('') + ylab("") + 
  theme(legend.position="none", strip.background = element_rect(fill="#c7dcf0"), strip.text = element_text(size=11)) +
  scale_fill_manual(values=campus.colors) + scale_x_continuous(breaks=seq(0,66,6), labels=seq(0,66,6))
```


## Non-Academic Hours
```{r, fig.height=8, fig.width=7}

```


## Total Workload Hours
```{r, fig.height=8, fig.width=7}

```



---

## [Student Demographics](Campus_Student_Demo.html)
*Click here to go to the Personal Demographics page.*

## [Personal Demographics](Campus_Personal_Demo.html)
*Click here to go to the Personal Demographics page.*