---
title: "Personal Demographics by Campus"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
source("common_code.R")
```
The following is a comparison across the 3 campuses (Chico, Fresno, and Northridge) for information relating to the personal demographics of the students.

## Age
```{r, fig.height=8, fig.width=7}
ggplot(data=bns, aes(x=age, fill=school)) + geom_histogram(bins = 23) + facet_wrap(~school, dir="v") + xlab('') + ylab("") + 
  theme(legend.position="none", strip.background = element_rect(fill="#c7dcf0"), strip.text = element_text(size=11)) +
  scale_fill_manual(values=campus.colors)
```
Looking at the age across each campus, it seems that again the distribution seems very similar for each. CSU Chico has an average age of `r unname(round(tapply(bns$age, bns$school, mean, na.rm=TRUE),2)[1])` years old, and a median of `r unname(round(tapply(bns$age, bns$school, median, na.rm=TRUE),2)[1])` years old. CSU Fresno has an average age of `r unname(round(tapply(bns$age, bns$school, mean, na.rm=TRUE),2)[2])` years old, and a median of `r unname(round(tapply(bns$age, bns$school, median, na.rm=TRUE),2)[2])` years old. CSU Northridge has an average age of `r unname(round(tapply(bns$age, bns$school, mean, na.rm=TRUE),2)[3])` years old, and a median of `r unname(round(tapply(bns$age, bns$school, median, na.rm=TRUE),2)[3])` years old.

## Gender
```{r, fig.height=4.6, fig.width=7}
plot_grpfrq(bns$q7, bns$school, wrap.labels = 20, wrap.legend.labels = 30, geom.colors = campus.colors, legend.title = "", show.prc = FALSE) + 
  xlab('') + theme(legend.position="top")
```
Looking at the distribution of gender across the campuses for survey participants, we can see that the majority of them are female. Chico seems to have the highest number of participants for each gender, with Fresno coming in second, and Northridge coming in behind them. 

## Ethnicity
```{r}
tmp <- bns %>% select(starts_with("eth_"), school)
tmp <- aggregate(.~school, tmp, sum)
rownames(tmp) <- tmp$school
tmp <- tmp %>% select(-school)
tmp <- as.data.frame(apply(tmp, 1, function(x) paste0(x, " (", percent(x/sum(x), accuracy = 0.1), ")")))
rownames(tmp) <- c('White','African American','American Indian','Chinese','Filipino','Asian Indian','Other Asian',
                   'Vietnamese','Korean','Japanese','Native Hawaiian','Samoan','Chamorro','Other Pacific Islander')

tmp %>% kable() %>% kable_styling(bootstrap_options = "striped")
```
It seems that for participants in the survey, over 50% identify as White for each campus. Both Chico and Fresno had their second most common ethnicity being Other Asian. Northridge had its second most common ethnicity being American Indian, closely followed by African American.

## Parents Education
```{r, fig.height=5.8, fig.width=7.6}
plot_grpfrq(bns$q13, bns$school, wrap.labels = 10, wrap.legend.labels = 30, geom.colors = campus.colors, legend.title = "", show.prc = FALSE) + 
  xlab('') + theme(legend.position="top")
```
It seems that for students with parents that have some type of college education (Associate's, Bachelor's, Master's) CSU Chico leads in all categories, followed by CSU Fresno, and finally CSU Northridge. CSU Chico also seems to have the most students whose parents had some college education, but no degree. CSU Fresno seems to have the most students who claim their parents highest level of education is less than high school. 

## First Generation
```{r, fig.height=4.6}
plot_grpfrq(bns$firstgen, bns$school, wrap.legend.labels = 30, geom.colors = campus.colors, legend.title = "", show.prc = FALSE) + 
  xlab('') + theme(legend.position="top")
```
Looking at the first generation students (see *Demographics: Personal Demographics* for definition of first generation students), we can see that CSU Chico seems to have the most first generation college students followed by Northridge and Fresno which are almost tied. It seems that Fresno has the most students that are not first gen, followed by Chico, and then Northridge.


---

## [Student Demographics](Campus_Student_Demo.html)
*Click here to go to the Personal Demographics page.*

## [Workload](Campus_Workload.html)
*Click here to go to the Workload page.*