---
title: "Workload by Campus"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
source("common_code.R")

tmp2 <- data.frame(q18=bns$q18, q19=bns$q19, q21=bns$q21, school=bns$school) %>% 
  mutate(q18=recode(q18, "22+"="22"), q18=as.numeric(q18),
         q19=recode(q19, "41+"="41"), q19=as.numeric(q19),
         q21=recode(q21, "41+"="41"), q21=as.numeric(q21))
tmp2$units <- tmp2$q18*3
tmp2$NonAcademic <- rowSums(tmp2[, c('q19','q21')], na.rm = TRUE)
tmp2$TotalHours <- rowSums(tmp2[, c('units','NonAcademic')], na.rm = TRUE)
```
The following is a comparison across the 3 campuses (Chico, Fresno, and Northridge) for information relating to the workload taken on by students, both academic and non-academic. This includes both paid/unpaid hours worked per week, as well as the academic workload taken on by students. A total of the hours worked each week is also looked at for each campus. The purpose is to see if any key differences are seen between the campuses, or if similar information is captured among them.

## Paid Hours Per Week
```{r, fig.height=4.6, fig.width=8.5}
bns$paid_work_hours <- fct_relevel(factor(bns$paid_work_hours), "0", "1-5", "6-10")

plot_grpfrq(bns$paid_work_hours, bns$school, wrap.legend.labels = 30, geom.colors = campus.colors, legend.title = "", show.prc = FALSE) + 
  xlab('') + theme(legend.position="top")
```


## Unpaid Hours Per Week
```{r, fig.height=4.6, fig.width=8.5}
bns$unpaid_work_hours <- fct_relevel(factor(bns$unpaid_work_hours), "0", "1-5", "6-10")

plot_grpfrq(bns$unpaid_work_hours, bns$school, wrap.legend.labels = 30, geom.colors = campus.colors, legend.title = "", show.prc = FALSE) + 
  xlab('') + theme(legend.position="top")
```


## Academic Hours
```{r, fig.height=5, fig.width=7}
# ggplot(data=tmp2, aes(x=units, fill=school)) + geom_histogram() + facet_wrap(~school, dir="v") + xlab('') + ylab("") + 
#   theme(legend.position="none", strip.background = element_rect(fill="#c7dcf0"), strip.text = element_text(size=11)) +
#   scale_fill_manual(values=campus.colors) + scale_x_continuous(breaks=seq(0,66,6), labels=seq(0,66,6))

tmp <- tmp2 %>% filter(units > 0)

plot_grpfrq(tmp$units, tmp$school, type="boxplot", title = "", wrap.legend.labels = 50, geom.colors = campus.colors, show.ci = TRUE) + 
  geom_jitter(width=0.15, alpha=0.4) + xlab("") + scale_y_continuous(breaks=seq(0,70,10), labels=seq(0,70,10)) + ylab('Academic Hours')
```
*Note: values corresponding to "22+" were rounded to 22. Values were also filtered so that only people who take classes (> 0 hours per week) were included.*

Looking at the academic hours across each campus, it seems that the distribution seems very similar for each. CSU Chico has an average unit workload of `r unname(round(tapply(tmp$units, tmp$school, mean, na.rm=TRUE),2)[1])` units, and a median of `r unname(round(tapply(tmp$units, tmp$school, median, na.rm=TRUE),2)[1])` units. CSU Fresno has an average unit workload of `r unname(round(tapply(tmp$units, tmp$school, mean, na.rm=TRUE),2)[2])` units, and a median of `r unname(round(tapply(tmp$units, tmp$school, median, na.rm=TRUE),2)[2])` units. CSU Northridge has an average unit workload of `r unname(round(tapply(tmp$units, tmp$school, mean, na.rm=TRUE),2)[3])` units, and a median of `r unname(round(tapply(tmp$units, tmp$school, median, na.rm=TRUE),2)[3])` units.

## Non-Academic Hours
```{r, fig.height=5, fig.width=7}
tmp <- tmp2 %>% filter(NonAcademic > 0)

# ggplot(data=tmp, aes(x=TotalHours, fill=school)) + geom_histogram(bins=41) + facet_wrap(~school, dir="v") + xlab('') + ylab("") + 
#   theme(legend.position="none", strip.background = element_rect(fill="#c7dcf0"), strip.text = element_text(size=11)) +
#   scale_fill_manual(values=campus.colors) + scale_x_continuous(breaks=seq(2,82,4), labels=seq(2,82,4))

plot_grpfrq(tmp$NonAcademic, tmp$school, type="boxplot", title = "", wrap.legend.labels = 50, geom.colors = campus.colors, show.ci = TRUE) + 
  geom_jitter(width=0.15, alpha=0.5) + xlab("") + scale_y_continuous(breaks=seq(0,90,10), labels=seq(0,90,10)) + ylab('Total Hours')
```
*Note: values corresponding to "41+" were rounded to 41. Values were also filtered so that only people who work (> 0 hours per week) were included.*

Looking at the non-academic hours across each campus, again it seems that the distribution are very similar for each. CSU Chico has an average non-academic workload of `r unname(round(tapply(tmp$TotalHours, tmp$school, mean, na.rm=TRUE),2)[1])` hours, and a median of `r unname(round(tapply(tmp$TotalHours, tmp$school, median, na.rm=TRUE),2)[1])` hours. CSU Fresno has an average non-academic workload of `r unname(round(tapply(tmp$TotalHours, tmp$school, mean, na.rm=TRUE),2)[2])` hours, and a median of `r unname(round(tapply(tmp$TotalHours, tmp$school, median, na.rm=TRUE),2)[2])` hours. CSU Northridge has an average non-academic workload of `r unname(round(tapply(tmp$TotalHours, tmp$school, mean, na.rm=TRUE),2)[3])` hours, and a median of `r unname(round(tapply(tmp$TotalHours, tmp$school, median, na.rm=TRUE),2)[3])` hours.

## Total Workload Hours
```{r, fig.height=5, fig.width=7}
tmp <- tmp2 %>% filter(TotalHours > 0)

plot_grpfrq(tmp$TotalHours, tmp$school, type="boxplot", title = "", wrap.legend.labels = 50, geom.colors = campus.colors, show.ci = TRUE) +
  geom_jitter(width=0.15, alpha=0.5) + xlab("") + scale_y_continuous(breaks=seq(0,150,15), labels=seq(0,150,15)) + ylab('Total Hours')
```
*Note: values corresponding to "41+" were rounded to 41, as well as values corresponding to "22+" being rounded to 22. Values were also filtered so that only people who work (> 0 hours per week) were included.*

Looking at the total workload hours across each campus, again it seems that the distribution are very similar for each. CSU Chico has an average total workload of `r unname(round(tapply(tmp$TotalHours, tmp$school, mean, na.rm=TRUE),2)[1])` hours, and a median of `r unname(round(tapply(tmp$TotalHours, tmp$school, median, na.rm=TRUE),2)[1])` hours. CSU Fresno has an average total workload of `r unname(round(tapply(tmp$TotalHours, tmp$school, mean, na.rm=TRUE),2)[2])` hours, and a median of `r unname(round(tapply(tmp$TotalHours, tmp$school, median, na.rm=TRUE),2)[2])` hours. CSU Northridge has an average total workload of `r unname(round(tapply(tmp$TotalHours, tmp$school, mean, na.rm=TRUE),2)[3])` hours, and a median of `r unname(round(tapply(tmp$TotalHours, tmp$school, median, na.rm=TRUE),2)[3])` hours. A small number of students also claim to work over 100 hours per week across academic and non-academic jobs.

---

## [Student Demographics](Campus_Student_Demo.html)
*Click here to go to the Personal Demographics page.*

## [Personal Demographics](Campus_Personal_Demo.html)
*Click here to go to the Personal Demographics page.*