---
title: "Eating Habits"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
source("common_code.R")
```

The following questions were asked in regards to students eating habits on a current, daily, and weekly basis. Students were asked how/if they prepare food at home, their daily consumption of fruits/vegetables and sugar, and their weekly habits of eating out and alcohol consumption. They were also asked about how confident they felt about buying/preparing healthy foods at home.

## Current Eating/Cooking Habits
**For each of the following statements, indicate how strongly you agree or disagree about your current eating and cooking habits:**
```{r, fig.height=6.5, fig.width=7.7}
questions <- bns %>% select(starts_with("q76_"))
names(questions) <- c("I do not regularly have access to a kitchen where I can prepare meals.",
                      "I have a secure place to store fresh food and pantry items.",
                      "I do not have enough room to store food items.",
                      "Thinking about food is stressful/causes anxiety.",
                      "I wish I had more food to eat.",
                      "I almost always skip meals.",
                      "I don't cook or shop for food.",
                      "No one cooks at home.",
                      "I do not think about my eating/food habits.")
plot_likert(questions,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
Figure 11.1: Current Eating and Cooking Habits

## Daily Consumption
### Fruits & Vegetables
**How many servings of fruits and vegetables do you usually consume per day? (not including fruit juices) `r print_n_reporting("fruit_veg_serv_daily")`**

*1 serving= 1 medium piece of fruit; 1/2 cup fresh, frozen, or canned fruits/vegetables; 1 cup salad greens; or 1/4 cup dried fruit.*
```{r, fig.height=3.5}
plot_frq(bns$fruit_veg_serv_daily) + xlab('Daily Fruit & Vegetable Servings')
```
Figure 11.2: Daily Fruit & Vegetable Consumption

Looking at the daily consumption of fruits and vegetables, the majority of people claim to eat between `r names(sort(table(bns$fruit_veg_serv_daily), decreasing = TRUE))[1]` servings (`r unname(sort(table(bns$fruit_veg_serv_daily), decreasing = TRUE))[1]` people). `r unname(sort(table(bns$fruit_veg_serv_daily), decreasing = TRUE))[2]` people claim to eat `r names(sort(table(bns$fruit_veg_serv_daily), decreasing = TRUE))[2]` servings, `r unname(sort(table(bns$fruit_veg_serv_daily), decreasing = TRUE))[3]` people claim to eat `r names(sort(table(bns$fruit_veg_serv_daily), decreasing = TRUE))[3]` servings, and `r unname(sort(table(bns$fruit_veg_serv_daily), decreasing = TRUE))[4]` people claim to eat `r names(sort(table(bns$fruit_veg_serv_daily), decreasing = TRUE))[4]` servings.

### Sugar/Energy Drinks
**How many ounces of regular soda/cola/pop, sports drink, or energy drinks do you consume each day? `r print_n_reporting("sugar_drinks_ounces_daily")`**
```{r, fig.width=7}
plot_frq(bns$sugar_drinks_ounces_daily) + xlab('Daily Sugar/Energy Drink Servings (Ounces)')
```
Figure 11.3: Daily Sugar/Energy Drink Consumption

Looking at daily consumption of regular soda/cola/pop, sports drink, or energy drinks the majority of people claim to drink `r names(sort(table(bns$sugar_drinks_ounces_daily), decreasing = TRUE))[1]` ounces (`r unname(sort(table(bns$sugar_drinks_ounces_daily), decreasing = TRUE))[1]` people). `r unname(sort(table(bns$sugar_drinks_ounces_daily), decreasing = TRUE))[2]` people claim to drink between `r names(sort(table(bns$sugar_drinks_ounces_daily), decreasing = TRUE))[2]` ounces, `r unname(sort(table(bns$sugar_drinks_ounces_daily), decreasing = TRUE))[3]` people claim to drink between `r names(sort(table(bns$sugar_drinks_ounces_daily), decreasing = TRUE))[3]`, and only a small number of participants claim to drink 17 or more ounces per day.

## Weekly Consumption
### Eating Out
**How frequently do you eat from fast food restaurants, convenience stores, or vending machines for a meal or meal replacement? `r print_n_reporting("eating_out_weekly")`**
```{r}
plot_frq(bns$eating_out_weekly) + xlab('Weekly Eating Out Frequency')
```
Figure 11.4: Weekly Eating Out Consumption

Looking at the weekly consumption of eating fast food, the majority of people claim to eat out `r names(sort(table(bns$eating_out_weekly), decreasing = TRUE))[1]` times per week (`r unname(sort(table(bns$eating_out_weekly), decreasing = TRUE))[1]` people). `r unname(sort(table(bns$eating_out_weekly), decreasing = TRUE))[2]` people claim to eat out `r names(sort(table(bns$eating_out_weekly), decreasing = TRUE))[2]` times, `r unname(sort(table(bns$eating_out_weekly), decreasing = TRUE))[3]` people claim to eat out `r names(sort(table(bns$eating_out_weekly), decreasing = TRUE))[3]` times, and only a small minority of people claim to eat out 5 or more times per week.

### Alcohol Consumption
**How often do you consume at least one serving of alcohol `r print_n_reporting("alc_consumption_weekly")` If consumed, how many servings of alcohol do you consume when you drink alcohol `r print_n_reporting("alc_servings_if_consumed")`**
```{r, fig.height=4.3, fig.width=8}
p1 <- plot_frq(bns$alc_consumption_weekly, ylim=c(0,310), title="How often do you consume alcohol:") +xlab('Days Consumed')
p2 <- plot_frq(bns$alc_servings_if_consumed, title="If consumed, how many servings:") + xlab('Number of Alcohol Servings')

grid.arrange(p1, p2, nrow=1)
rm(p1,p2)
```
Figure 11.5: Weekly Alcohol Consumption - Days & Servings

Looking at the weekly alcohol consumption, the majority of people claim to consume alcohol `r names(sort(table(bns$alc_consumption_weekly), decreasing = TRUE))[1]` days per week (`r unname(sort(table(bns$alc_consumption_weekly), decreasing = TRUE))[1]` people). `r unname(sort(table(bns$alc_consumption_weekly), decreasing = TRUE))[2]` people claim to drink `r names(sort(table(bns$alc_consumption_weekly), decreasing = TRUE))[2]` days per week. Only a small number of people claim to drink 3 or more days per week. Of the people who do consume alcohol, the majority consume `r names(sort(table(bns$alc_servings_if_consumed), decreasing = TRUE))[1]` servings (`r unname(sort(table(bns$alc_servings_if_consumed), decreasing = TRUE))[1]` people). `r unname(sort(table(bns$alc_servings_if_consumed), decreasing = TRUE))[2]` people claim to drink `r names(sort(table(bns$alc_servings_if_consumed), decreasing = TRUE))[2]` servings,  `r unname(sort(table(bns$alc_servings_if_consumed), decreasing = TRUE))[3]` people claim to drink `r names(sort(table(bns$alc_servings_if_consumed), decreasing = TRUE))[3]` servings, and only a small number drink 5 or more servings.

## Food Comfort
**The following questions pertain to how comfortable you feel about buying or preparing food:**
```{r, fig.width=8}
questions <- bns %>% select(starts_with("q82_"))
names(questions) <- c("How confident are you that you can use the same healthy ingredient in more than one meal?",
                      "How confident are you that you can use basic cooking skills, like cutting fruits and vegetables, measuring out ingredients, or following a recipe?",
                      "How confident are you that you can buy healthy foods for your family on a budget?",
                      "How confident are you that you can cook healthy foods for your family on a budget?")
plot_likert(questions,
            grid.range = c(1, 1),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 5,
            geom.colors = likert.pal.5,
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
Figure 11.6: Buying/Preparing Food Comfort 


---

## [Physical Activity](Physical_Activity.html)
*Click here to go to the Physical Activity page.*

## [Mental Health](Mental_Health.html)
*Click here to go to the Mental Health page.*

## [Sleep](Sleep.html)
*Click here to go to the Sleep page.*


