---
title: "Personal Demographics"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---


```{r, include=FALSE}
source("common_code.R")
page.num <- 1
```

The following set of questions were asked in regards to the students' personal demographics. This includes the students' age at the time of the survey (2020), ethnicities they identify as, and the number of dependents they are responsible for taking care of. They were also asked about parents' education, which will help us identify first generation college students based on certain criteria.

<br>

## Age
*The following was determined by taking the difference between birth date and the time at which the survey was completed `r print_n_reporting('age')`*
```{r}
hist_with_box('age', 93, 15, 0.3, 1, c(0,105), 'Age (Years)')
```
`r fig.cap(page.num, "Student Age Distribution")`

The age for participants in the survey range from `r min(bns$age, na.rm = TRUE)` to `r max(bns$age, na.rm = TRUE)` at the time of completion, with the majority of participants being between 20-30 years old. The average age of a participant in this survey is `r round(mean(bns$age, na.rm = TRUE),1)` years old.

<br />

### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click here for campus breakdown of age distribution. </summary>
```{r, fig.height=7 ,fig.width=7}
ggplot(bns, aes(x=age, group=school, fill=school)) + geom_histogram(aes(y=..density..), color="black", position = "identity")  +
  geom_density(alpha=0.4, color="black") + ylim(0, 0.23) + 
  facet_wrap(~school, dir="v", scales='free') + xlab('Age (Years)') + ylab("Density") + 
  theme(legend.position="none", strip.background = element_rect(fill="#c7dcf0"), strip.text = element_text(size=11)) +
  scale_fill_manual(values=campus.colors)
```
`r fig.cap(page.num, "Age Distribution by Campus")`

Breaking down age across each campus, the data indicates that the distribution are very similar for each. Chico State has an average age of `r unname(round(tapply(bns$age, bns$school, mean, na.rm=TRUE),2)[1])` years old, and a median of `r unname(round(tapply(bns$age, bns$school, median, na.rm=TRUE),2)[1])` years old. Fresno State has an average age of `r unname(round(tapply(bns$age, bns$school, mean, na.rm=TRUE),2)[2])` years old, and a median of `r unname(round(tapply(bns$age, bns$school, median, na.rm=TRUE),2)[2])` years old. CSU, Northridge has an average age of `r unname(round(tapply(bns$age, bns$school, mean, na.rm=TRUE),2)[3])` years old, and a median of `r unname(round(tapply(bns$age, bns$school, median, na.rm=TRUE),2)[3])` years old.
</details>
<br />

## Gender Identity
**What is your gender identity? `r print_n_reporting('q7')`**

<div class = "row">
<div class = "col-md-7">
```{r, fig.height=3.5, fig.width=4.5}
plot_frq(bns$q7, sort.frq="desc") + xlab('Gender') + ylab("Frequency")
```
</div>
  
<div class = "col-md-4">
<br><br><br>`r fig.cap(page.num, "Student Gender Identity")` <br>

Of the survey participants, `r unname(table(bns$q7)['Woman'])` of them identify as a woman, `r unname(table(bns$q7)['Man'])` identify as a man, and `r unname(table(bns$q7)['Gender non-binary, non-conforming'])` identify as gender non-binary, non-conforming. There are also survey participants who preferred not to answer.
</div>
</div>

<br />

### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click here for campus breakdown of gender distribution. </summary>
```{r, fig.height=4.6, fig.width=7}
bns %>% select(school, q7) %>% filter(!is.na(q7)) %>% count(q7, school) %>% group_by(school) %>% 
  mutate(freq = paste0("(", percent(n/sum(n), accuracy = 0.1), ")")) %>% 
  ggplot(data = ., aes(x=school, y=n, fill=q7)) + geom_bar(width=0.7, position = position_dodge(width=0.9), stat="identity") + 
  xlab('') + ylab("Frequency") + theme(legend.position="top") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) + 
  scale_fill_manual(labels = function(x) str_wrap(x, width = 20), name="Gender Identity", 
                    values=RColorBrewer::brewer.pal(8, "Set2")) + 
  geom_text(position=position_dodge(width=0.9), aes(y=n + 12, label=n)) + 
  geom_text(position=position_dodge(width=0.9), aes(y=n + 5, label=freq))
```

`r fig.cap(page.num, "Gender Identification by Campus")`

The breakdown of the distribution for gender across each campuses indicates that the majority of survey participants are female. Chico State seems to have the highest number of participants for each gender, Fresno State has the highest proportion of female survey participants, and CSU, Northridge has the highest proportion of male survey participants. 
</details>
<br />

## Ethnicity
**In the US Census, Hispanic Origins are not races. Do you identify as Hispanic or Latino or Spanish Origin? `r print_n_reporting('q8')`**

<div class = "row">
<div class = "col-md-6">
```{r, fig.height=3, fig.width=4}
tmp <- data.frame(q8=bns$q8) %>% mutate(hispanic=as.factor(ifelse(is.na(q8), NA, ifelse(grepl("Yes", q8), "Yes", "No")))) %>% select(-q8)

plot_frq(tmp$hispanic) + xlab("") + ylab("Frequency")
```
</div>
  
<div class = "col-md-5">
<br><br>`r fig.cap(page.num, "Hispanic Origin Identification")` <br>

We define Hispanic Origin to include: Mexican, Mexican American, Chicano, Puerto Rican, or another Hispanic/Latino/Spanish origin. The data indicates that the majority of survey participants identify as some type of Hispanic Origins (`r unname(table(tmp$hispanic)['Yes'])` people), while around a quarter of them do not identify as having Hispanic Origins (`r unname(table(tmp$hispanic)['No'])` people).
</div>
</div>

<br />

### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click here for campus breakdown of ethnicity distribution. </summary>
```{r}
tmp <- data.frame(q8=bns$q8, school=bns$school) %>% 
  mutate(hispanic=as.factor(ifelse(is.na(q8), NA, ifelse(grepl("Yes", q8), "Yes", "No"))),
         school=ifelse(is.na(hispanic), NA, school)) %>% select(-q8)
```

```{r, fig.height=4.5, fig.width=7}
tmp %>% select(school, hispanic) %>% filter(!is.na(hispanic)) %>% count(hispanic, school) %>% group_by(school) %>% 
  mutate(freq = paste0("(", percent(n/sum(n), accuracy = 0.1), ")")) %>% 
  ggplot(data = ., aes(x=school, y=n, fill=hispanic)) + geom_bar(width=0.7, position = position_dodge(width=0.9), stat="identity") + 
  xlab('') + ylab("Frequency") + theme(legend.position="top") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) + 
  scale_fill_manual(labels = function(x) str_wrap(x, width = 20), name="Hispanic Origin", 
                    values=RColorBrewer::brewer.pal(8, "Set2")) + 
  geom_text(position=position_dodge(width=0.9), aes(y=n + 12, label=n)) + 
  geom_text(position=position_dodge(width=0.9), aes(y=n + 5, label=freq))
```
`r fig.cap(page.num, "Hispanic Origin Identification by Campus")`

Breaking down Hispanic origin for each campus, the data indicates that most of the campuses have approximately the same number of survey participants who do identify as having Hispanic origin. CSU, Northridge also has the highest proportion of survey participants who have Hispanic origin. Looking at survey participants who do not identify as having Hispanic origin, Chico State seems to have the most (`r table(tmp$hispanic, tmp$school)["No","California State University, Chico"]` people), followed by Fresno State, and finally CSU, Northridge. 
</details>
<br />

## Race
```{r}
tmp <- bns %>% select(starts_with("eth_")) %>% mutate(white=ifelse(is.na(eth_white), NA, ifelse(eth_white == 1, 1, 0)),
                                                      black=ifelse(is.na(eth_african_amer), NA, ifelse(eth_african_amer == 1, 1, 0)),
                                                      amer_indian=ifelse(is.na(eth_amer_inidian), NA, ifelse(eth_amer_inidian == 1, 1, 0)),
                                                      asian=ifelse((is.na(eth_chinese) | is.na(eth_filipino) | is.na(eth_asian_indian) |
                                                                      is.na(eth_other_asian) | is.na(eth_vietnamese) | is.na(eth_korean) |
                                                                      is.na(eth_japanese)), NA, 
                                                                   ifelse((eth_chinese == 1 | eth_filipino == 1 | eth_asian_indian  == 1 |
                                                                      eth_other_asian == 1 | eth_vietnamese == 1 | eth_korean == 1 |
                                                                      eth_japanese == 1), 1, 0)),
                                                      hawaiian=ifelse((is.na(eth_pacific_islander) | is.na(eth_chamorro) | is.na(eth_hawaiian) |
                                                                         is.na(eth_samoan)), NA, 
                                                                       ifelse((eth_pacific_islander == 1 | eth_chamorro == 1 | eth_hawaiian == 1 |
                                                                        eth_samoan == 1), 1, 0))) %>% select(15:19)
```
**What race do you identify as? Select all that apply `r print_n_reporting_tmp('white')`** *Note that races were collapsed from an original 14 options down to 5 broad groups defined by [census.gov](https://www.census.gov/quickfacts/fact/note/US/RHI625219).*

Table 1.1: Student Race Identification
```{r}
cnames <- c("White", "Black or African American", "American Indian and Alaska Native", "Asian", "Native Hawaiian and Other Pacific Islander")
tmp2 <- tmp %>% na.omit()
colnames(tmp2) <- cnames
tmp2 <- as.data.frame(t(tmp2)) %>% mutate(sums=rowSums(.),
                                          label=paste0(sums, " (", percent(sums/ncol(.), accuracy=0.1), ")")) %>% arrange(desc(sums)) %>% select(label)
colnames(tmp2) <- "Yes (%)"
tmp2 %>% kable() %>% kable_styling(bootstrap_options = "striped")
```

### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click here for campus breakdown of race distribution. </summary>
```{r}
tmp <- bns %>% select(starts_with("eth_"), school) %>% mutate(white=ifelse(is.na(eth_white), NA, ifelse(eth_white == 1, 1, 0)),
                                                              black=ifelse(is.na(eth_african_amer), NA, ifelse(eth_african_amer == 1, 1, 0)),
                                                              amer_indian=ifelse(is.na(eth_amer_inidian), NA, ifelse(eth_amer_inidian == 1, 1, 0)),
                                                              asian=ifelse((is.na(eth_chinese) | is.na(eth_filipino) | is.na(eth_asian_indian) |
                                                                              is.na(eth_other_asian) | is.na(eth_vietnamese) | is.na(eth_korean) |
                                                                              is.na(eth_japanese)), NA, 
                                                                           ifelse((eth_chinese == 1 | eth_filipino == 1 | eth_asian_indian  == 1 |
                                                                                     eth_other_asian == 1 | eth_vietnamese == 1 | eth_korean == 1 |
                                                                                     eth_japanese == 1), 1, 0)),
                                                              hawaiian=ifelse((is.na(eth_pacific_islander) | is.na(eth_chamorro) | is.na(eth_hawaiian) |
                                                                                 is.na(eth_samoan)), NA, 
                                                                              ifelse((eth_pacific_islander == 1 | eth_chamorro == 1 | eth_hawaiian == 1 |
                                                                                        eth_samoan == 1), 1, 0))) %>% select(15:20)

rnames <- c("White", "Black or African American", "American Indian and Alaska Native", "Asian", "Native Hawaiian and Other Pacific Islander")
tmp2 <- tmp %>% na.omit()
tmp2 <- tmp2 %>% group_by(school) %>% summarise(across(where(is.numeric), sum)) %>% t() %>% 
  janitor::row_to_names(row_number = 1) %>% as.data.frame()
tmp2 <- as.data.frame(sapply(tmp2, as.numeric))
tmp2 <- as.data.frame(apply(tmp2, 2, function(x) paste0(x, " (", percent(x/sum(x), accuracy = 0.1), ")")))
rownames(tmp2) <- rnames

tmp2 %>% kable() %>% kable_styling(bootstrap_options = "striped")
rm(tmp,tmp2)
```
Table 1.2: Race Identification by Campus

For survey participants at each campus, the data indicates that over 50% identify as White for each. Both Chico State and Fresno State have their next most common ethnicity being Other Asian. CSU, Northridge had its second most common ethnicity being American Indian, closely followed by African American.
</details>
<br />


## Dependents
**If you have dependents, then how many of them receive more than 50% of their financial support from you? `r print_n_reporting('q11')`**
```{r, fig.height=3.5, fig.width=5.5}
plot_frq(bns$q11) + xlab('Number of Dependents') + ylab("Frequency")
```
`r fig.cap(page.num, "Number of Dependents")`

The majority of survey participants claim to have 0 dependents (`r unname(table(bns$q11)['0'])` people). `r unname(table(bns$q11)['1'])` survey participants claim to have only 1 dependent, and only `r nrow(bns[bns$q11 > 1, 'q11'] %>% na.omit())` claim to have 2 or more dependents.

<br>

### Dependent Ages
**What is/are the age(s) of these dependent(s)?**
```{r, fig.height=4, fig.width=7}
dep.ages <- as.numeric(unname(unlist(bns %>% select(starts_with('q12_')))) %>% na.omit())
dep.ages.df <- data.frame(Ages=dep.ages) # wouldn't compile in a single line for some reason

plot_frq(dep.ages.df$Ages, type='histogram', show.mean = TRUE, ylim=c(0,32), xlim=c(0,103), show.mean.val = FALSE, show.sd = FALSE) +
  geom_boxplot(data=dep.ages.df, aes(x=Ages, y=28), alpha=0.6, width=5, fill="#336699") +
  geom_jitter(data=dep.ages.df, aes(x=Ages, y=28), position=position_jitter(height=2)) +
  xlab('Dependent Ages (Years)') + ylab("Frequency")
```
`r fig.cap(page.num, "Dependent Age Distribution")`

From figure 1.8, the data indicates that the majority of dependents are under the age of 18. The ages of these dependents ranges from `r min(dep.ages)` to `r max(dep.ages)` with a standard deviation of `r round(sd(dep.ages),2)`. The average age for a dependent is `r round(mean(dep.ages),2)` while the median age is `r round(median(dep.ages),2)`. The most common dependent age is `r names(sort(table(dep.ages), decreasing=TRUE)[1])` years old, with `r unname(sort(table(dep.ages), decreasing=TRUE)[1])` parents having dependents of this age.

<br>

## Parents Education
**What is the highest level of education completed by your parents/guardians? `r print_n_reporting('q13')`**
```{r, fig.height=4.5, fig.width=8}
tmp <- as.data.frame(table(bns$q13)) %>% 
  mutate(Percent=lapply(Freq, function(x) paste0('(', percent(x/sum(!is.na(bns[['q13']])), accuracy = 0.1), ')')),
         FirstGen=as.character(c(1,0,1,1,1,0,0,1)),
         Var1=recode(Var1, "Other/Unknown" = "Other/ Unknown")) %>% arrange((desc(Freq)))

ggplot(tmp, aes(x=factor(Var1, levels=Var1), y=Freq, fill=FirstGen, label=Percent)) + geom_col(colour = "black") + 
  scale_fill_manual(values=c("#336699", "#ecf0b7")) + geom_text(aes(y=Freq+13)) + ylim(0,220) + 
  scale_x_discrete(labels=label_wrap(10)) +   geom_text(aes(y=Freq + 29, label=Freq)) + 
  xlab('') + ylab("Frequency") + theme(legend.position = "none")
```
`r fig.cap(page.num, "Parents Highest Education")`

*Note: Variables filled with yellow above are used to show the conditions used to build the First Generation variable*.

The highest level of education completed by most survey participants parents is "`r names(sort(table(bns$q13), decreasing=TRUE)[1])`" (`r unname(sort(table(bns$q13), decreasing=TRUE)[1])`). `r unname(sort(table(bns$q13), decreasing=TRUE)[2])` survey participants claim their parents highest level is "`r names(sort(table(bns$q13), decreasing=TRUE)[2])`", and `r unname(sort(table(bns$q13), decreasing=TRUE)[3])` claim their parents highest level is "`r names(sort(table(bns$q13), decreasing=TRUE)[3])`". Only a minority of survey participants have parents who have some type of college level degree.

<br />

### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click here for campus breakdown of parents education distribution. </summary>
```{r, fig.height=6, fig.width=8}
# plot_grpfrq(bns$school, bns$q13, wrap.labels = 25, wrap.legend.labels = 26, geom.colors = RColorBrewer::brewer.pal(8, "Set2"),
#             legend.title = "", show.prc = FALSE) + xlab('') + ylab("Frequency") +  
#   theme(legend.position="top", legend.key = element_rect(size = 6), legend.key.size = unit(1, "cm"))

bns %>% select(school, q13) %>% filter(!is.na(q13)) %>% count(q13, school) %>% group_by(school) %>% 
  mutate(freq = paste0("(", percent(n/sum(n), accuracy = 0.1), ")")) %>% 
  ggplot(data = ., aes(x=school, y=n, fill=q13)) + geom_bar(width=0.7, position = position_dodge(width=0.9), stat="identity") + 
  xlab('') + ylab("Frequency") + theme(legend.position="right") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) + 
  scale_fill_manual(labels = function(x) str_wrap(x, width = 20), name=" ", 
                    values=RColorBrewer::brewer.pal(8, "Set2")) + ylim(0,90) +
  geom_text(position=position_dodge(width=0.9), aes(y=n + 11, label=paste0(n, " ", freq))) + coord_flip()
```
`r fig.cap(page.num, "Parents Highest Education by Campus")`

Breaking down parents education for each campus, the data indicates that Chico State has the highest number of students with parents that have some type of college degree or education (Associate's, Bachelor's, Master's, Some college). Fresno State has the highest proportion of survey participants with parents whose education is less than high school. CSU, Northridge has the highest proportion of students parents who have a high school diploma or GED.

</details>
<br />

### First Generation
*Note: students with parents education identified as "Other/Unknown" were not marked as first gen or not since they could not be determined.* **`r print_n_reporting('firstgen')`**

<div class = "row">
<div class = "col-md-6">
```{r, fig.height=3, fig.width=4}
tmp <- data.frame(firstgen=bns$firstgen) %>% 
  mutate(firstgen=factor(ifelse(is.na(firstgen), NA, ifelse(firstgen == 0, "Not First Gen", "First Gen")), levels=c("Not First Gen", "First Gen")))

plot_frq(tmp$firstgen, ylim=c(0,440)) + xlab('') + ylab("Frequency")
```
</div>
  
<div class = "col-md-5">
<br><br><br>`r fig.cap(page.num, "First Generation College Students")` <br>

According to figure 1.11, we can see that `r unname(sort(table(bns$firstgen), decreasing=TRUE)[1])` survey participants are considered as First Generation College students and `r unname(sort(table(bns$firstgen), decreasing=TRUE)[2])` survey participants are not considered First Generation College students. 
</div>
</div>

As defined by the [University of California](https://www.universityofcalifornia.edu/sites/default/files/First-Generation%20Student%20Success%20at%20UC%208-2017.pdf), we define first generation students as "working to be part of the first generation in their families to earn a four-year university degree". This means based upon parents education, students in the data set are considered first generation if their parents do not have a Bachelor's or Master's degree from a four-year university. From the *Parents Education* graph, all bars highlighted as yellow are considered first gen, while all bars in blue are not (excluding Other/Unknown).

<br />

#### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click here for campus breakdown of first generation student distribution. </summary>
```{r, fig.height=4.6}
tmp <- data.frame(firstgen=bns$firstgen, school=bns$school) %>% 
  mutate(firstgen=factor(ifelse(is.na(firstgen), NA, ifelse(firstgen == 0, "Not First Gen", "First Gen")), levels=c("Not First Gen", "First Gen")))

tmp %>% select(school, firstgen) %>% filter(!is.na(firstgen)) %>% count(firstgen, school) %>% group_by(school) %>% 
  mutate(freq = paste0("(", percent(n/sum(n), accuracy = 0.1), ")")) %>% 
  ggplot(data = ., aes(x=school, y=n, fill=firstgen)) + geom_bar(width=0.7, position = position_dodge(width=0.9), stat="identity") + 
  xlab('') + ylab("Frequency") + theme(legend.position="top") +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) + 
  scale_fill_manual(labels = function(x) str_wrap(x, width = 20), name="Status", 
                    values=RColorBrewer::brewer.pal(8, "Set2")) + ylim(0,160) +
  geom_text(position=position_dodge(width=0.9), aes(y=n + 16, label=n)) + 
  geom_text(position=position_dodge(width=0.9), aes(y=n + 7, label=freq))
```
`r fig.cap(page.num, "First Generation College Students by Campus")`

Breaking down first generation students for each campus, the data indicates that even though Chico State has the highest number of first generation college students, they also have the lowest proportion of first generation college students. CSU, Northridge has the highest proportion of first generation college students, as well as the lowest proportion of students who are not considered first gen.
</details>
<br />

---

## [Student Demographics](Student_Demo.html)
*Click here to go to the Student Demographics page.*

