---
title: "Personal Demographics"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---


```{r, include=FALSE}
source("common_code.R")
```

The following set of questions were asked in regards to the students personal demographics. This includes the students age at the time of the survey (2020), ethnicities they identify as, and the number of dependents they are responsible for taking care of. They were also asked about parents education, which will help us identify first generation college students based on certain criteria.

## Age
```{r}
hist_with_box('age', 93, 15, 0.3, 1, c(0,105), 'Age')
```
The age for participants in the survey range from `r min(bns$age, na.rm = TRUE)` to `r max(bns$age, na.rm = TRUE)` at the time of completion, with the majority of participants being between 20-30 years old. The average age of a participant in this survey is `r round(mean(bns$age, na.rm = TRUE),1)` years old.

## Gender Identity
**What is your gender identity?**
```{r}
plot_frq(bns$q7, sort.frq="desc") + xlab('Gender')
```
Of the people who participated in the survey, `r unname(table(bns$q7)['Woman'])` of them identify as a Woman, `r unname(table(bns$q7)['Man'])` identify as a Man, and `r unname(table(bns$q7)['Gender non-binary, non-conforming'])` identify as Gender non-binary, non-conforming. There are also people who preferred not to answer.

## Ethnicity
**In the US Census, Hispanic Origins are not races. Do you identify as Hispanic or Latino or Spanish Origin?**
```{r}
plot_frq(bns$q8, wrap.labels = 15, ylim=c(0,280), sort.frq="desc") + xlab('')
```
Looking at the above graph we see `r unname(table(bns$q8)['Yes, Mexican, Mexican American, Chicano'])` people identify as Mexican, Mexican American, or Chicano. `r unname(table(bns$q8)['No, not Hispanic, Latino or Spanish Origin'])` people do no identify as Hispanic, Latin, or Spanish Origin. `r unname(table(bns$q8)['Yes, another Hispanic, Latino or Spanish Origin'])` people identify as another Hispanic, Latino, or Spanish Origin. `r unname(table(bns$q8)['Yes, Puerto Rican'])` people identify as Puerto Rican.

### *Proposed Collapse (Ethnicity)*
**In the US Census, Hispanic Origins are not races. Do you identify as Hispanic or Latino or Spanish Origin?**
```{r, fig.height=2, fig.width=8}
tmp <- data.frame(q8=bns$q8) %>% mutate(hispanic=as.factor(ifelse(is.na(q8), NA, ifelse(grepl("Yes", q8), "Yes", "No")))) %>% select(-q8)
xlbl <- "Do you identify as Hispanic or Latino or Spanish Origin?"

plot_likert(tmp,
            axis.labels = xlbl,
            grid.range = c(1.05, 1.05),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 2,
            geom.colors = c("#D8B365","#5AB4AC"),
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
For the above graph, Hispanic Origin includes: Mexican, Mexican American, Chicano, Puerto Rican, or another Hispanic/Latino/Spanish origin. It seems that the majority of people identify as some type of Hispanic Origins (`r unname(table(tmp$hispanic)['Yes'])` people), while around a quarter of them do not identify as having Hispanic Origins (`r unname(table(tmp$hispanic)['No'])` people).

```{r}
rm(tmp) # remove data set
```

## Race
**What race do you identify as? (Select all that apply).**
```{r, fig.height=5, fig.width=8}
question <- "eth"
qlabels <- c('White','African American','American Indian','Chinese','Filipino','Asian Indian','Other Asian',
             'Vietnamese','Korean','Japanese','Native Hawaiian','Samoan','Chamorro','Other Pacific Islander')

ethnicity_vars <- prep_binary_vars(question, qlabels)

# Plot table of percentages
ethnicity_vars %>% 
  select(Measure = xlab, "Yes (%)" = pct_lab) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped")

# Create bar plot of values & percentage 
# ethnicity_vars %>% 
#   ggplot(aes(x=xlab, y=x, label = pct_lab)) + 
#     geom_col(fill=primary.chc.col) + 
#     geom_text(aes(y=x+15), size=3.6) +
#     scale_y_continuous(breaks = seq(0,200,20), labels=seq(0,200,20), limits = c(0,180)) +
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) + xlab("") + ylab("")
```


## Marital Status
**What is your marital status?**
```{r}
plot_frq(bns$q10, wrap.labels = 10, sort.frq="desc") + xlab('Marital Status')
```
The above graph tells us that the majority of people (`r unname(table(bns$q10)['Single, never married'])`) are single or never been married. `r unname(table(bns$q10)['Married'])` people are married, and `r unname(table(bns$q10)['Living with a partner'])` are living with a partner.

## Dependents
**If you have dependents, then how many of them receive more than 50% of their financial support from you?**
```{r}
plot_frq(bns$q11) + xlab('Number of Dependents')
```
The majority of people who participated in the survey (`r unname(table(bns$q11)['0'])`) claim to have 0 dependents. `r unname(table(bns$q11)['1'])` people claim to have only 1 dependent, and only `r nrow(bns[bns$q11 > 1, 'q11'] %>% na.omit())` people have 2 or more dependents.

### Dependent Ages
**What is/are the age(s) of these dependent(s)?**
```{r, fig.height=4.5, fig.width=7}
dep.ages <- as.numeric(unname(unlist(bns %>% select(starts_with('q12_')))) %>% na.omit())
dep.ages.df <- data.frame(Ages=dep.ages) # wouldn't compile in a single line for some reason

plot_frq(dep.ages.df$Ages, type='histogram', show.mean = TRUE, ylim=c(0,30), xlim=c(0,103), show.mean.val = FALSE, show.sd = FALSE) +
  geom_jitter(data=dep.ages.df, aes(x=Ages, y=27), position=position_jitter(height=2)) + 
  geom_boxplot(data=dep.ages.df, aes(x=Ages, y=27), alpha=0.6, width=5, fill="#336699") + xlab('Dependent Ages (Years)')
```
From the above graphs, the majority of dependents are under the age of 18. The ages of these dependents ranges from `r min(dep.ages)` to `r max(dep.ages)` with a standard deviation of `r round(sd(dep.ages),2)`. The average age for a dependent is `r round(mean(dep.ages),2)` while the median value is `r round(median(dep.ages),2)`. The most common dependent age is `r names(sort(table(dep.ages), decreasing=TRUE)[1])`, which appears `r unname(sort(table(dep.ages), decreasing=TRUE)[1])` times in the data.

## Parents Education
**What is the highest level of education completed by your parents/guardians?**
```{r, fig.height=4.5, fig.width=8}
tmp <- as.data.frame(table(bns$q13)) %>% 
  mutate(Percent=lapply(Freq, function(x) paste0('(', percent(x/sum(!is.na(bns[['q13']])), accuracy = 0.1), ')')),
         FirstGen=as.character(c(1,0,1,1,1,0,0,1)),
         Var1=recode(Var1, "Other/Unknown" = "Other/ Unknown")) %>% arrange((desc(Freq)))

ggplot(tmp, aes(x=factor(Var1, levels=Var1), y=Freq, fill=FirstGen, label=Percent)) + geom_col(colour = "black") + 
  scale_fill_manual(values=c("#336699", "#ecf0b7")) + geom_text(aes(y=Freq+13)) + ylim(0,220) + 
  scale_x_discrete(labels=label_wrap(10)) +   geom_text(aes(y=Freq + 29, label=Freq)) + 
  xlab('') + ylab('') + theme(legend.position = "none")
```
*Note: Variables filled with yellow above are used to show the conditions used to build the First Generation variable in the next plot*.

The highest level of education completed by most students parents is `r names(sort(table(bns$q13), decreasing=TRUE)[1])` (`r unname(sort(table(bns$q13), decreasing=TRUE)[1])`). `r unname(sort(table(bns$q13), decreasing=TRUE)[2])` students claim their parents highest level is `r names(sort(table(bns$q13), decreasing=TRUE)[2])`, and `r unname(sort(table(bns$q13), decreasing=TRUE)[3])` students claim their parents highest level is `r names(sort(table(bns$q13), decreasing=TRUE)[3])`. Only a minority of students have parents who have some type of college level degree.

### First Generation
*Note: students with parents education identified as "Other/Unknown" were not marked as first gen or not since they could not be determined.*
```{r}
tmp <- data.frame(firstgen=bns$firstgen) %>% 
  mutate(firstgen=factor(ifelse(is.na(firstgen), NA, ifelse(firstgen == 0, "Not First Gen", "First Gen")), levels=c("Not First Gen", "First Gen")))

plot_frq(tmp$firstgen, ylim=c(0,420)) + xlab('')
```
As defined by the [University of California](https://www.universityofcalifornia.edu/sites/default/files/First-Generation%20Student%20Success%20at%20UC%208-2017.pdf), we define first generation students as "working to be part of the first generation in their families to earn a four-year university degree". This means based upon parents education, students in the data set are considered first generation if their parents do not have a Bachelor's or Master's degree from a four-year university. From the *Parents Education* graph, all bars highlighted as yellow are considered first gen, while all bars in blue are not (excluding Other/Unknown).

From this information, we can see that `r unname(sort(table(bns$firstgen), decreasing=TRUE)[1])` students who participated in the survey are First Generation College students and `r unname(sort(table(bns$firstgen), decreasing=TRUE)[2])` students are not First Generation College students. 

---

## [Student Demographics](Student_Demo.html)
*Click here to go to the Student Demographics page.*

