---
title: "Physical Activity"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
source("common_code.R")
page.num <- 9
```

The following questions were asked in regards to their physical activity over the past week. Students were asked to select how many days in the last week they had done any of the following exercise types: moderate, vigorous, or strength training.[^1]

<br>

## Past 7 Days

The following three questions were asked in regards to participants physical activity over the past 7 days:
```{r, fig.width=8}
tmp1 <- cbind(data.frame(Question=rep("Moderate Exercise", 8)), as.data.frame(table(bns[["moderate_exercise_past_week"]])))
tmp2 <- cbind(data.frame(Question=rep("Vigorous Exercise", 8)), as.data.frame(table(bns[["vigorous_exercise_past_week"]])))
tmp3 <- cbind(data.frame(Question=rep("Strength Training", 8)), as.data.frame(table(bns[["strength_training_past_week"]])))
pa.data <- rbind(tmp1, tmp2, tmp3)
colnames(pa.data) <- c('Type', 'Days', 'Freq')
rm(tmp1, tmp2, tmp3)

ggplot(pa.data) +
    geom_linerange(aes(x = Days, ymin = 0, ymax = Freq, colour = Type), 
                   position = position_dodge(width = 0.6), size=1) +
    geom_point(aes(x = Days, y = Freq, colour = Type),
               position = position_dodge(width = 0.6), size=2.5) + scale_color_manual(values=c("#336699", "#000000", "#b5d43b")) +
  labs(colour='Exercise Type') + xlab('Number of Days') + ylab('') + theme_bw() +
  theme(legend.key.size = unit(1, 'cm'), 
        legend.key.height = unit(1, 'cm'), 
        legend.key.width = unit(1, 'cm'), 
        legend.title = element_text(size=13),
        legend.text = element_text(size=11))
```
`r fig.cap(page.num, "Weekly Physical Activity")`

<br>

```{r, results='asis'}
tmp <- data.frame(rbind(table(bns$moderate_exercise_past_week),
                        table(bns$strength_training_past_week),
                        table(bns$vigorous_exercise_past_week)))

tmp <- as.data.frame(apply(tmp, 1, function(x) paste0(x, " (", percent(x/sum(x), accuracy = 0.1), ")")))
colnames(tmp) <- c("**Moderate Exercise**", "**Strength Training**", "**Vigorous Training**")
tmp["**Days**"] <- 0:7
tmp <- tmp[c(4,1,2,3)]

t(tmp) %>% kable() %>% kable_styling(bootstrap_options = "striped") 
```
Table 9.1: Weekly Physical Activity Breakdown

<br>

### Moderate Exercise
How often did you do **moderate-intensity** cardio or aerobic exercise (caused a noticeable increase in heart rate, such as brisk walk) for at least 30 minutes? `r print_n_reporting("moderate_exercise_past_week")`

- The majority of participants claim to have done `r names(sort(table(bns$moderate_exercise_past_week), decreasing = TRUE))[1]` days of moderate exercise in the past week (`r unname(sort(table(bns$moderate_exercise_past_week), decreasing = TRUE))[1]` people). The general trend is that as the number of days increases, the number of students who exercised for those given number of days decreases. This seems to be the most commonly performed type of exercise from the graph above (typically the highest number of days per week out of all exercise types).

### Strength Training 
How often did you do 8-10 **strength training** exercises (such as resistance weight machines) for at least 8 repetitions each? `r print_n_reporting("strength_training_past_week")`

- The majority of participants claim to have done `r names(sort(table(bns$strength_training_past_week), decreasing = TRUE))[1]` days of strength training in the past week (`r unname(sort(table(bns$strength_training_past_week), decreasing = TRUE))[1]` people). The general trend is that as the number of days increases, the number of students who exercised for those given number of days decreases. Only a small number of people claim to do strength training for 3 or more days in the past week.

### Vigorous Exercise
How often did you do **vigorous-intensity** cardio or aerobic exercise (caused large increases in breathing or heart rate, such as jogging) for at least 20 minutes? `r print_n_reporting("vigorous_exercise_past_week")`

- The majority of participants claim to have done `r names(sort(table(bns$vigorous_exercise_past_week), decreasing = TRUE))[1]` days of vigorous exercise in the past week (`r unname(sort(table(bns$vigorous_exercise_past_week), decreasing = TRUE))[1]` people). The general trend is that as the number of days increases, the number of students who exercised for those given number of days decreases. Only a small number of people claim to do vigorous exercise for 4 or more days in the past week.

--- 

[^1]: These questions were developed based on the [Surgeon General's physical activity guidelines for adults](https://health.gov/sites/default/files/2019-09/Physical_Activity_Guidelines_2nd_edition.pdf) who recommend: 150 minutes to 300 minutes a week of moderate-intensity exercise, 75 minutes to 150 minutes a week of vigorous-intensity aerobic exercise, or an equivalent combination of moderate- and vigorous-intensity aerobic activity. They also recommend strength-training activities on 2 or more days a week.


## [Eating Habits](Eating_Habits.html)
*Click here to go to the Eating Habits page.*

## [Mental Health](Mental_Health.html)
*Click here to go to the Mental Health page.*

## [Sleep](Sleep.html)
*Click here to go to the Sleep page.*
