---
title: "Sleep"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
source("common_code.R")
page.num <- 10
```

The following questions were asked in regard to students' sleep patterns. This includes their average nightly sleep during the academic year (week and weekend), if they feel sleep deprived, and what the causes of their sleep deprivation come from. They were also asked if they are tired at work/school, how often they are tired there, and if they have fallen asleep in class in the past year. 

<br>

## Academic Year
**On average, during the academic year, how many hours of sleep do you get in a typical 24-hour period?**[^1] *Note that for the week days we have `r print_n_reporting("q84")` And for the weekends we have `r print_n_reporting("q85")`* 

#### During the Week (Monday-Friday)
```{r, fig.height=3.5, fig.width=7}
hist_with_box('q84', 145, 24, 0.4, NULL, c(0,162), 'Number of Hours')
```
`r fig.cap(page.num, "Weekday Hours of Sleep Distribution")`

<br>

#### During the Weekend (Saturday-Sunday)
```{r, fig.height=3.5, fig.width=7}
hist_with_box('q85', 108, 17, 0.4, NULL, c(0,122), 'Number of Hours')
```
`r fig.cap(page.num, "Weekend Hours of Sleep Distribution")`

During the week, students claim to get an average (denoted by the dotted line) of `r round(mean(bns$q84, na.rm = TRUE), 2)` hours per night, with a median of `r round(median(bns$q84, na.rm = TRUE), 2)` hours. During the weekend, students claim to get an average (denoted by the dotted line) of `r round(mean(bns$q85, na.rm = TRUE), 2)` hours per night, with a median of `r round(median(bns$q85, na.rm = TRUE), 2)` hours. Students get an average of `r round(mean(bns$q85, na.rm = TRUE), 2)-round(mean(bns$q84, na.rm = TRUE), 2)` more hours of sleep on the weekend versus during the week.

<br>

## Sleep Deprived
**On average, how many times per month do you feel deprived of sleep? `r print_n_reporting("q86")`**
```{r}
hist_with_box('q86', 55, 6, 0.4, NULL, c(0,61), 'Days Per Month')
```
`r fig.cap(page.num, "Sleep Deprivation Distribution")`

Students claim that on average they were feeling sleep deprived (denoted by the dotted line) for `r round(mean(bns$q86, na.rm = TRUE), 1)` days out of the month, with a median of `r round(median(bns$q86, na.rm = TRUE), 1)` days per month. 

<br>

### Causes of Sleep Deprivation
**Select the activities that cause you to feel deprived of sleep (Select all that apply).**
```{r, fig.height=4.7, fig.width=7.2}
question <- "sleep_loss"
qlabels <- c("Studying or finishing coursework.",
             "Working a paid, unpaid job or internship.",
             "Attending social activities or events.",
             "Spending time with family or friends.",
             "Watching movies, playing games, social media etc.",
             "Other")
sleep_loss_vars <- prep_binary_vars(question, qlabels)

# Plot table of Percentages
sleep_loss_vars %>% 
  select(Measure = xlab, "Yes (%)" = pct_lab) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped")

# Create bar plot of values & percentage 
# sleep_loss_vars %>% 
#   ggplot(aes(x=xlab, y=pct, label = pct_lab)) + 
#     geom_col(fill=primary.chc.col) + 
#     geom_text(aes(y=pct+.065)) +
#     scale_y_continuous(limits = c(0,1), labels=percent) + 
#     scale_x_discrete(labels=label_wrap(13)) + xlab("") + ylab("Percent")
```
Table 10.1: Causes of Sleep Deprivation Breakdown

<br>

## Tired at Work/School
**How frequently do you feel tired while at work or school? `r print_n_reporting("q88")`**

<div class = "row">
<div class = "col-md-7">
```{r, fig.height=3.5, fig.width=4.5}
plot_frq(bns$q88) + xlab('How Often') + ylab("Frequency")
```
</div>
  
<div class = "col-md-4">
<br><br><br>`r fig.cap(page.num, "Frequency of Tired at Work/School")` <br>

The most common response that people felt tired at work or school was `r tolower(names(sort(table(bns$q88), decreasing = TRUE))[1])` (`r unname(sort(table(bns$q88), decreasing = TRUE))[1]` people). `r unname(sort(table(bns$q88), decreasing = TRUE))[2]` people claimed that they were `r tolower(names(sort(table(bns$q88), decreasing = TRUE))[2])` tired, `r unname(sort(table(bns$q88), decreasing = TRUE))[3]` people claimed that they were `r tolower(names(sort(table(bns$q88), decreasing = TRUE))[3])` tired, and `r unname(sort(table(bns$q88), decreasing = TRUE))[4]` people claimed that they were `r tolower(names(sort(table(bns$q88), decreasing = TRUE))[4])` tired.
</div>
</div>

<br>

## Fallen Asleep in Class
**Have you fallen asleep in class in the past 12 months? `r print_n_reporting("q89")`**

<div class = "row">
<div class = "col-md-6">
```{r, fig.height=3, fig.width=4}
plot_frq(bns$q89, ylim=c(0,260)) + xlab('') + ylab("Frequency")
```
</div>
  
<div class = "col-md-5">
<br><br><br>`r fig.cap(page.num, "Fallen Asleep in Class (Past Year)")` <br> 

The majority of students (`r unname(sort(table(bns$q89), decreasing = TRUE)['No'])` people) claim that they have not fallen asleep in class in the past year, while `r unname(sort(table(bns$q89), decreasing = TRUE)['Yes'])` people claim that they have fallen asleep in class.
</div>
</div>

[^1]: This question was developed by the [Behavioral Risk Factor Surveillance System (BRFSS)](https://www.cdc.gov/brfss/questionnaires/pdf-ques/2018_BRFSS_English_Questionnaire.pdf) designed by the Centers for Disease Control and Prevention (CDC).

---

## [Eating Habits](Eating_Habits.html)
*Click here to go to the Eating Habits page.*

## [Physical Activity](Physical_Activity.html)
*Click here to go to the Physical Activity page.*

## [Mental Health](Mental_Health.html)
*Click here to go to the Mental Health page.*
