---
title: "Student Demographics"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
source("common_code.R")
```

The following set of questions were asked in regards to the students academic demographic. This includes information such as what Cal State University they are currently enrolled in, their class standing, major, GPA, and enrolled units. They were also asked questions about programs they participate in as well as what type of student they are (transfer, international, etc.) to help identify groups of students.

## School
```{r}
plot_frq(bns$school, ylim=c(0,180)) + xlab('School')
```
Three schools participated in this pilot of the survey: `r names(sort(table(bns$school), decreasing=TRUE)[1])` (`r unname(sort(table(bns$school), decreasing=TRUE)[1])`), `r names(sort(table(bns$school), decreasing=TRUE)[2])` (`r unname(sort(table(bns$school), decreasing=TRUE)[2])`), and C`r names(sort(table(bns$school), decreasing=TRUE)[3])` (`r unname(sort(table(bns$school), decreasing=TRUE)[3])`). From the above graph, it seems that students from each campus will be nearly equally represented in the data.

## Class Standing
**Estimate your class standing by units completed**
```{r, fig.width=8}
plot_frq(bns$academic_level, wrap.labels = 10) + xlab('Class Standing')
```
It seems that the majority of the people are either in their Junior (`r unname(sort(table(bns$academic_level), decreasing=TRUE)['Junior (60-89 semester units)'])` people) or Senior (`r unname(sort(table(bns$academic_level), decreasing=TRUE)['Senior (90+ semester units)'])` people) semester. There are a few Sophomores and very few Freshman or higher education students.

## Major
**What is your major?**
```{r, fig.height=5, fig.width=8.2}
bns <- bns %>% mutate(q16=recode(q16, 
                                 "Science, Technology, Engineering and Math (STEM) (Includes Medicine, Computer Science, Agriculture, Accounting, Statistics, Nursing, and Nutrition)" = "Science, Technology, Engineering and Math (STEM)"))

plot_frq(bns$q16, ylim=c(0,190), wrap.labels = 20, sort.frq = 'desc') + xlab('')
```
The majority of students in the data seem to be majoring in some type of `r names(sort(table(bns$q16), decreasing=TRUE)[1])` program (`r unname(sort(table(bns$q16), decreasing=TRUE)[1])` people). `r unname(sort(table(bns$q16), decreasing=TRUE)[2])` of the students are `r names(sort(table(bns$q16), decreasing=TRUE)[2])` majors. Students were also given the option of "Other" to fill in a major if it did not fall into one of the above categories and of the `r unname(sort(table(bns$q16), decreasing=TRUE)['Other'])` who selected this, `r unname(colSums(!is.na(bns))['q16_6_text'])` gave their responses below.

### Other Majors
```{r}
cnames <- c('Other Majors', 'Percent')
qs <- unique(bns$q16_6_text) %>% na.omit()
question_table('q16_6_text', qs, cnames)
```

## Overall GPA
**What is your approximate overall grade point average (GPA)?**
```{r}
plot_frq(bns$q17) + xlab('GPA')
```
The most common GPA for the data ranges between `r names(sort(table(bns$q17), decreasing=TRUE)[1])` (`r unname(sort(table(bns$q17), decreasing=TRUE)[1])` students), followed by`r names(sort(table(bns$q17), decreasing=TRUE)[2])` (`r unname(sort(table(bns$q17), decreasing=TRUE)[2])` students). There are also `r unname(sort(table(bns$q17), decreasing=TRUE)[3])` students who have an overall GPA between `r names(sort(table(bns$q17), decreasing=TRUE)[3])`. 

## Currently Enrolled Units
**How many units are you currently taking?**
```{r, fig.width=7}
xlbls <- c(as.character(0:21), "22+")
bns <- bns %>% mutate(q18=recode(q18, "22+"="22"),
                      q18=as.numeric(q18))

plot_frq(bns$q18, type='histogram', show.prc = FALSE, show.n = FALSE) + scale_x_continuous(breaks=0:22, labels=xlbls) + xlab('Units')
```
*Note that "22+" was rounded for 22 in the following analysis for the currently enrolled number of units*. 

The average number of units that a student in this data is enrolled in is `r round(mean(bns$q18, na.rm = TRUE), 2)` units, while the median is `r median(bns$q18, na.rm = TRUE)` units. It seems that the majority of students are considered full-time (12 or more units), with `r names(sort(table(bns$q18), decreasing=TRUE)[1])` units being most common and `r names(sort(table(bns$q18), decreasing=TRUE)[2])` units following that.

## Student Identifiers

The following questions were asked as a series of Yes/No Responses to help further understand students. They were grouped together in this page by the start of the question.

### I identify as...
```{r}
questions <- c(paste0('q14_', 1:2), paste0('q14_', 5:15))
rnames <- c("A Transfer Student", "LGBTQA+", "A student with a disability", "A former foster youth/child",
            "An International student", "A non-California resident (not International)",
            "An Upward Bound, Educational Talent Search, AVID, TRIO, or other college preparation program alumni student",
            "An EOP (Educational Opportunity Program) student", "An ESL (English as a Second Language) student",
            "A Veteran of military service", "A student athlete", "A DREAM (i.e. undocumented) student",
            "A DACA (i.e. Deferred Action for Childhood Arrivals) student")
binary_table(questions, "Yes", rnames, ".")
```

### Disability Support Services (??)
*Note*: This name varies by campus and may not always be called the Disability Support Service Center.
```{r, fig.height=5, fig.width=7}
questions <- paste0('q14_', 3:4)
rnames <- c('I receive services through the Disability Support Services Center',
            'I have NOT received services through the Disability Support Services Center')
binary_table(questions, "Yes", rnames, ".")
```

### I participate in...
```{r}
questions <- paste0('q14_', 18:21)
rnames <- c('CalWorks (i.e. TANF or cash aid for needy families) or Aid to Families with Dependent Children (AFDC)',
            'The Job Opportunities and Basic Skills (JOBS) program',
            'The CalFresh Employment or Training (CFET) Program',
            'The Greek system. (i.e. sorority, fraternity)')
binary_table(questions, "Yes", rnames, ".")
```

### I am...
```{r}
questions <- c(paste0('q14_', 16:17), paste0('q14_', 22:26), paste0('q101_', 1:2))
rnames <- c('Approved, awarded, or accepted for work study (with or without a work study job)',
            'Currently a Pell Grant recipient', 'Enrolled in Workforce Innovation and Opportunity Act (WIOA)',
            'Enrolled in the Mathematics, Engineering, Science achievement (MESA) program',
            paste0('Enrolled in a program that increases employability for current and former foster youth ',
                   '(PATH Scholars, Educational Opportunity Resilient Scholars Program (RSP), Renaissance Scholars Program)'),
            'The parent/guardian of a dependent household member between the age of 6 and 12 with no adequate childcare',
            'A single parent of a dependent household member under the age of 12',
            'Enrolled in a Teaching Credential Program', 'Enrolled in the School of Social Work Practicum Program (Field work program)')
binary_table(questions, "Yes", rnames, ".")
```

---

## [Personal Demographics](Personal_Demo.html)
*Click here to go to the Personal Demographics page.*

