---
title: "Workload"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---


```{r, include=FALSE}
source("common_code.R")
```

The following questions were asked in regards to the weekly workload taken on by students. This includes work from both paid/unpaid jobs, as well as time spent caregiving for a family member. Students academic workload is also looked at in order to see the hours spent each week on school work, as well as looking at the combined hours across academic and non-academic responsibilities. 

## Weekly Paid Work Hours
**Estimate the number of hours you work in a PAID job (for example, server at a restaurant, office assistant, etc.) or paid internship (for example, training, shadowing, or practicum) per week.**
```{r}
bns$paid_work_hours <- fct_relevel(factor(bns$paid_work_hours), "0", "1-5", "6-10")

plot_frq(bns$paid_work_hours, ylim=c(0,150)) + xlab('Paid Hours Per Week')
```
It seems that the majority of people work either part-time or not at all. Only a small number of people are considered to be working full-time (40 or more hours per week). Below is a breakdown of the exact paid hours worked by survey participants as well as the impacts that COVID had on their hours. 

### Exact Hours Breakdown
Although the majority of the participants claim to work 0 hours per week, below is a breakdown of the exact number of hours for those who claim to work a paid job:
```{r, fig.width=8.5}
xlbls <- c(as.character(seq(1,40,5)), "41+")

tmp <- data.frame(q19=bns$q19) %>% mutate(q19=recode(q19, "41+"="41"), q19=as.numeric(q19)) %>%
  filter(q19 > 0)

plot_frq(tmp$q19, type='histogram', geom.size = 1, xlim = c(1,20), show.prc = FALSE, show.n = FALSE, 
         show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
    geom_boxplot(data=tmp, aes(x=q19, y=45), alpha=0.8, width=6, fill="#587db6") +
    geom_jitter(data=tmp, aes(x=q19, y=45), position=position_jitter(width=2, height=2.2), alpha=0.7) +
  scale_x_continuous(breaks=c(seq(1,40,5), 41), labels=xlbls) + xlab('Weekly Hours')
```
*Note that "41+" was rounded for 41 in the following analysis for the paid hours worked per week*. 

The average number of paid hours worked per week (denoted by the dotted line) is `r round(mean(tmp$q19, na.rm = TRUE), 2)`, while the median is `r median(tmp$q19, na.rm = TRUE)` hours. It seems that the majority of students are considered part-time workers (less than 40 hours per week), with `r names(sort(table(tmp$q19), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$q29), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$q19), decreasing=TRUE)[2])` hours following that.

### Impact of COVID
**Have the hours you work in a PAID job or internship changed due to COVID-19?**
```{r, fig.width=8}
plot_frq(bns$q20, ylim=c(0,135), wrap.labels = 20, sort.frq = 'desc') + xlab('')
```
With the impact of COVID, it seems that most people were able to keep their current paid jobs with only slight changes. `r unname(table(bns$q20)['Yes, my hours have decreased but I still have a job.'])` people had their hours decrease, `r unname(table(bns$q20)['No, my hours have remained the same.'])` people maintained the same hours, and `r unname(table(bns$q20)['Yes, my hours have increased and I still have a job or I have a new job.'])` people had their hours increase. There was also `r unname(table(bns$q20)['Yes, I no longer have my job/internship.'])` people who claimed that they no longer had their paid position due to the impact of COVID, while `r unname(table(bns$q20)['I did not have a job or internship before COVID-19 and I still do not.'])` people also claimed that they did not have a paid position before COVID.

## Unpaid Work Hours
**Estimate the number of hours you work in an UNPAID internship (for example, training, shadowing, practicum, and/or volunteer, etc.). Do not combine with answers above. **
```{r, fig.height=4.5}
bns$unpaid_work_hours <- fct_relevel(factor(bns$unpaid_work_hours), "0", "1-5", "6-10")

plot_frq(bns$unpaid_work_hours) + xlab('Unpaid Hours Per Week')
```
We can see that the majority of people (`r unname(table(bns$unpaid_work_hours)['0'])`) do not work an unpaid job. A small number of people work part-time at an unpaid job and only a select few people work full-time at an unpaid job. Below is a breakdown of the number of unpaid hours worked per week.

### Exact Hours Breakdown
Although the majority of the participants claim to work 0 hours per week, below is a breakdown of the exact number of hours for those who claim to work a unpaid job:
```{r, fig.width=8.5}
tmp <- data.frame(q21=bns$q21) %>% mutate(q21=recode(q21, "41+"="41"), q21=as.numeric(q21)) %>%
  filter(q21 > 0)

plot_frq(tmp$q21, type='histogram', geom.size = 1, xlim = c(1,20), ylim=c(0,18), show.prc = FALSE, show.n = FALSE, 
         show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
    geom_boxplot(data=tmp, aes(x=q21, y=15), alpha=0.8, width=2.5, fill="#587db6") +
    geom_jitter(data=tmp, aes(x=q21, y=15), position=position_jitter(width=1.2, height=1), alpha=0.7) +
  scale_x_continuous(breaks=c(seq(1,40,5), 41), labels=xlbls) + xlab('Weekly Hours')
```
*Note that "41+" was rounded for 41 in the following analysis for the unpaid hours worked per week*. 

The average number of unpaid hours worked per week (denoted by the dotted line) is `r round(mean(tmp$q21, na.rm = TRUE), 2)`, while the median is `r median(tmp$q21, na.rm = TRUE)` hours. It seems that the majority of students do not work unpaid positions, with `r names(sort(table(tmp$q21), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$q21), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$q21), decreasing=TRUE)[2])` hours following that.

## Unpaid Caregiving Hours
**Estimate the number of hours you spend each week on unpaid family obligations (for example, taking care of younger siblings, preparing family meals, running errands for the family, etc.)**
```{r}
bns$caregiving_hours <- fct_relevel(factor(bns$caregiving_hours), "0", "1-5", "6-10")

plot_frq(bns$caregiving_hours) + xlab('Unpaid Caregiving Hours Per Week')
```
It seems that the majority of people in the data do spend some time each week caring for family members. Only `r unname(table(bns$caregiving_hours)['0'])` people estimated that they spent 0 hours per week for family obligations. There are also around the same number of people who estimated they work full-time (40 or more hours per week) on these family obligations. Below is a breakdown of these unpaid hours spent on family obligations each week.

### Exact Hours Breakdown
Although some of the participants claim to work 0 hours per week, below is a breakdown of the exact number of hours for those who claim to spend time on unpaid family obligations:
```{r, fig.width=8.5}
tmp <- data.frame(q22=bns$q22) %>% mutate(q22=recode(q22, "41+"="41"), q22=as.numeric(q22)) %>%
  filter(q22 > 0)

plot_frq(tmp$q22, type='histogram', geom.size = 1, xlim = c(1,20), show.prc = FALSE, show.n = FALSE, 
         show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
    geom_boxplot(data=tmp, aes(x=q22, y=53), alpha=0.8, width=8, fill="#587db6") +
    geom_jitter(data=tmp, aes(x=q22, y=53), position=position_jitter(width=1.5, height=3), alpha=0.7) +
  scale_x_continuous(breaks=c(seq(1,40,5), 41), labels=xlbls) + xlab('Weekly Hours')
```
*Note that "41+" was rounded for 41 in the following analysis for the unpaid caregiving hours worked per week*. 

The average number of unpaid caregiving hours worked per week (denoted by the dotted line) is `r round(mean(tmp$q22, na.rm = TRUE), 2)`, while the median is `r median(tmp$q22, na.rm = TRUE)` hours. There does not seem to be a clear pattern in the number of unpaid caregiving hours worked, with `r names(sort(table(tmp$q22), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$q22), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$q22), decreasing=TRUE)[2])` hours following that (`r unname(sort(table(tmp$q22), decreasing=TRUE)[2])` people). 

## Academic Workload
Below is a breakdown of the academic workload (using the 3 hours of work per unit measurement).
```{r, fig.width=7}
tmp <- data.frame(q18 = bns$q18)

if (!is.numeric(tmp$q18)) {
  tmp <- tmp %>% mutate(q18=recode(q18, "22+"="22"), q18=as.numeric(q18))
}
tmp <- tmp %>% mutate(q18 = q18*3)

plot_frq(tmp$q18, type='histogram', show.prc = FALSE, show.n = FALSE, show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
  geom_boxplot(data=tmp, aes(x=q18, y=125), alpha=0.8, width=15, fill="#587db6") +
  geom_jitter(data=tmp, aes(x=q18, y=125), position=position_jitter(width=1.5, height=6.8), alpha=0.7) + 
  scale_x_continuous(breaks=seq(0,66,3), labels=seq(0,66,3)) + xlab('Academic Hours Per Week')
```
The average number of academic hours worked per week (denoted by the dotted line) is `r round(mean(tmp$q18, na.rm = TRUE), 2)`, while the median is `r median(tmp$q18, na.rm = TRUE)` hours. The majority of students do seem to be working 36 or more hours per week, with `r names(sort(table(tmp$q18), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$q18), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$q18), decreasing=TRUE)[2])` hours following that (`r unname(sort(table(tmp$q18), decreasing=TRUE)[2])` people). 

## Non-Academic Workload
Below is a combination of both paid and unpaid hours worked by students to get a further understanding of the workload participants face on a weekly basis. The values are also filtered so that only people who worked (more than 0 hours in total) were included.
```{r, fig.width=7}
tmp <- data.frame(q19=bns$q19, q21=bns$q21)

if (!is.numeric(tmp$q19) & !is.numeric(tmp$q21)) {
  tmp <- tmp %>% mutate(q19=recode(q19, "41+"="41"), q19=as.numeric(q19),
                        q21=recode(q21, "41+"="41"), q21=as.numeric(q21))
}

tmp$TotalHours <- rowSums(tmp, na.rm = TRUE)
tmp <- tmp %>% filter(TotalHours > 0)

plot_frq(tmp$TotalHours, type='histogram', geom.size=1, xlim=c(2,82), ylim=c(0,55), show.prc = FALSE, 
         show.n = FALSE, show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
  geom_boxplot(data=tmp, aes(x=TotalHours, y=45), alpha=0.8, width=7, fill="#587db6") +
  geom_jitter(data=tmp, aes(x=TotalHours, y=45), position=position_jitter(width=1.5, height=3), alpha=0.7) + 
  scale_x_continuous(breaks=seq(2,82, 5), labels=seq(2,82, 5)) + xlab('Total Work Hours Per Week')
```
The average number of total hours worked per week (denoted by the dotted line) is `r round(mean(tmp$TotalHours, na.rm = TRUE), 2)`, while the median is `r median(tmp$TotalHours, na.rm = TRUE)` hours. The majority of students do seem to be working under 40 hours per week in total, with `r names(sort(table(tmp$TotalHours), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$TotalHours), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$TotalHours), decreasing=TRUE)[2])` hours following that (`r unname(sort(table(tmp$TotalHours), decreasing=TRUE)[2])` people). 

## Total Workload
Below is a combination of all worked hours per week, both academic and non-academic. This includes units (3 hr/unit), paid, and unpaid worked hours.
```{r, fig.width=8}
tmp <- data.frame(q18=bns$q18, q19=bns$q19, q21=bns$q21)

if (!is.numeric(tmp$q18) & !is.numeric(tmp$q19) & !is.numeric(tmp$q21)) {
  tmp <- tmp %>% mutate(q18=recode(q18, "22+"="22"), q18=as.numeric(q18),
                        q19=recode(q19, "41+"="41"), q19=as.numeric(q19),
                        q21=recode(q21, "41+"="41"), q21=as.numeric(q21))
}
tmp <- tmp %>% mutate(q18=q18*3)

tmp$TotalHours <- rowSums(tmp, na.rm = TRUE)
tmp <- tmp %>% filter(TotalHours > 0)

plot_frq(tmp$TotalHours, type='histogram', geom.size=1.9, ylim=c(0,55), show.prc = FALSE, 
         show.n = FALSE, show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
  geom_boxplot(data=tmp, aes(x=TotalHours, y=45), alpha=0.8, width=7, fill="#587db6") +
  geom_jitter(data=tmp, aes(x=TotalHours, y=45), position=position_jitter(width=1.5, height=3), alpha=0.7) + 
  scale_x_continuous(breaks=floor(seq(10,135,12.5)), labels=floor(seq(9,134,12.5))) + xlab('Total Hours Per Week')
```
The average number of total hours worked per week (denoted by the dotted line) is `r round(mean(tmp$TotalHours, na.rm = TRUE), 2)`, while the median is `r median(tmp$TotalHours, na.rm = TRUE)` hours. The majority of students do seem to be working over full-time in total, with `r names(sort(table(tmp$TotalHours), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$TotalHours), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$TotalHours), decreasing=TRUE)[2])` hours following that (`r unname(sort(table(tmp$TotalHours), decreasing=TRUE)[2])` people).

```{r}
rm(tmp) # remove tmp data set
```



