---
title: "Workload"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---


```{r, include=FALSE}
source("common_code.R")

page.num <- 3

tmp2 <- data.frame(q18=bns$q18, q19=bns$q19, q21=bns$q21, school=bns$school) %>% 
  mutate(q18=recode(q18, "22+"="22"), q18=as.numeric(q18),
         q19=recode(q19, "41+"="41"), q19=as.numeric(q19),
         q21=recode(q21, "41+"="41"), q21=as.numeric(q21))
tmp2$units <- tmp2$q18*3
tmp2$NonAcademic <- ifelse(is.na(tmp2[,'q19']) & is.na(tmp2[,"q21"]), NA,  rowSums(tmp2[, c('q19','q21')], na.rm = TRUE))
tmp2$TotalHours <- ifelse(is.na(tmp2[, 'units']) & is.na(tmp2[,'NonAcademic']), NA,  rowSums(tmp2[, c('units','NonAcademic')], na.rm = TRUE))
```

The following questions were asked in regards to the weekly workload taken on by students. This includes work from both paid/unpaid jobs, as well as time spent caregiving for a family member. Students academic workload is also looked at in order to see the hours spent each week on school work, as well as looking at the combined hours across academic and non-academic responsibilities. 

## Weekly Paid Work Hours
**Estimate the number of hours you work in a PAID job (for example, server at a restaurant, office assistant, etc.) or paid internship (for example, training, shadowing, or practicum) per week. `r print_n_reporting('paid_work_hours')`**
```{r}
bns$paid_work_hours <- fct_relevel(factor(bns$paid_work_hours), "0", "1-5", "6-10")

plot_frq(bns$paid_work_hours, ylim=c(0,150)) + xlab('Paid Hours Per Week')
```
`r fig.cap(page.num, "Weekly Paid Hour Ranges")`

It seems that the majority of people work either part-time or not at all. Only a small number of people are considered to be working full-time (40 or more hours per week). Below is a breakdown of the exact paid hours worked by survey participants as well as the impacts that COVID had on their hours. 

### Exact Hours Breakdown
```{r}
# filtered data before printing n and %
tmp <- data.frame(q19=bns$q19) %>% mutate(q19=recode(q19, "41+"="41"), q19=as.numeric(q19)) %>%
  filter(q19 > 0)
```

Although the majority of the participants claim to work 0 hours per week, below is a breakdown of the exact number of hours for those who claim to work a paid job `r print_n_reporting_tmp("q19")`
```{r, fig.width=8.5}
xlbls <- c(as.character(seq(1,40,5)), "41+")

plot_frq(tmp$q19, type='histogram', geom.size = 1, xlim = c(1,20), show.prc = FALSE, show.n = FALSE, 
         show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
    geom_boxplot(data=tmp, aes(x=q19, y=45), alpha=0.8, width=6, fill="#587db6") +
    geom_jitter(data=tmp, aes(x=q19, y=45), position=position_jitter(width=2, height=2.2), alpha=0.7) +
  scale_x_continuous(breaks=c(seq(1,40,5), 41), labels=xlbls) + xlab('Weekly Hours')
```
`r fig.cap(page.num, "Weekly Paid Hours Distribution")`

*Note that "41+" was rounded for 41 in the following analysis for the paid hours worked per week*. 

The average number of paid hours worked per week (denoted by the dotted line) is `r round(mean(tmp$q19, na.rm = TRUE), 2)`, while the median is `r median(tmp$q19, na.rm = TRUE)` hours. It seems that the majority of students are considered part-time workers (less than 40 hours per week), with `r names(sort(table(tmp$q19), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$q29), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$q19), decreasing=TRUE)[2])` hours following that.

<br />

### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click arrow for campus breakdown of paid weekly hours. </summary>
```{r}
tmp <- tmp2 %>% filter(q19 > 0)
```
**`r print_n_reporting_tmp('q19')`** *Note: below hours were filtered to only include people that worked (> 0 hours) a paid job. The value "41+" was also rounded to 41 for the graph/calculations.* 
```{r, fig.height=7, fig.width=7}
ggplot(tmp, aes(x=q19, group=school, fill=school, color=school)) + geom_histogram(aes(y=..density..), color="black", position = "identity")  +
  geom_density(alpha=0.4, color="black") + facet_wrap(~school, dir="v", scales='free') + xlab('Weekly Paid Hours') + ylab("Density") + 
  theme(legend.position="none", strip.background = element_rect(fill="#c7dcf0"), strip.text = element_text(size=11)) +
  scale_fill_manual(values=campus.colors) + scale_color_manual(values=campus.colors) + 
  scale_x_continuous(breaks=seq(1,41,5), labels=c(as.character(seq(1,36,5)), "41+"))

```
`r fig.cap(page.num, "Weekly Paid Hour Distribution by Campus")`

Looking at the breakdown of both graphs, the distribution of paid weekly hours worked across all campuses seem to be mostly similar. CSU Northridge has a mean value of `r unname(round(tapply(tmp$q19, tmp$school, mean)[3],2))` hours and a median of `r unname(round(tapply(tmp$q19, tmp$school, median)[3],2))` hours.  CSU Fresno, which seems to have students who tend to work more hours, has a mean value of `r unname(round(tapply(tmp$q19, tmp$school, mean)[2],2))` hours and a median of `r unname(round(tapply(tmp$q19, tmp$school, median)[2],2))` hours. CSU Chico has a mean value of `r unname(round(tapply(tmp$q19, tmp$school, mean)[1],2))` hours and a median of `r unname(round(tapply(tmp$q19, tmp$school, median)[1],2))` hours.

</details>
<br />

### Impact of COVID
**Have the hours you work in a PAID job or internship changed due to COVID-19? `r print_n_reporting('q20')`**
```{r, fig.width=8}
plot_frq(bns$q20, ylim=c(0,135), wrap.labels = 20, sort.frq = 'desc') + xlab('')
```
`r fig.cap(page.num, "COVID Impact on Paid Hours")`

With the impact of COVID, it seems that most people were able to keep their current paid jobs with only slight changes. `r unname(table(bns$q20)['Yes, my hours have decreased but I still have a job.'])` people had their hours decrease, `r unname(table(bns$q20)['No, my hours have remained the same.'])` people maintained the same hours, and `r unname(table(bns$q20)['Yes, my hours have increased and I still have a job or I have a new job.'])` people had their hours increase. There was also `r unname(table(bns$q20)['Yes, I no longer have my job/internship.'])` people who claimed that they no longer had their paid position due to the impact of COVID, while `r unname(table(bns$q20)['I did not have a job or internship before COVID-19 and I still do not.'])` people also claimed that they did not have a paid position before COVID.

## Unpaid Work Hours
**Estimate the number of hours you work in an UNPAID internship (for example, training, shadowing, practicum, and/or volunteer, etc.). Do not combine with answers above. `r print_n_reporting('unpaid_work_hours')`**
```{r, fig.height=4.5}
bns$unpaid_work_hours <- fct_relevel(factor(bns$unpaid_work_hours), "0", "1-5", "6-10")

plot_frq(bns$unpaid_work_hours) + xlab('Unpaid Hours Per Week')
```
`r fig.cap(page.num, "Weekly Unpaid Hour Ranges")`

We can see that the majority of people (`r unname(table(bns$unpaid_work_hours)['0'])`) do not work an unpaid job. A small number of people work part-time at an unpaid job and only a select few people work full-time at an unpaid job. Below is a breakdown of the number of unpaid hours worked per week.

### Exact Hours Breakdown
```{r}
# filtered data before printing n and %
tmp <- data.frame(q21=bns$q21) %>% mutate(q21=recode(q21, "41+"="41"), q21=as.numeric(q21)) %>%
  filter(q21 > 0)
```
Although the majority of the participants claim to work 0 hours per week, below is a breakdown of the exact number of hours for those who claim to work a unpaid job `r print_n_reporting_tmp("q21")`
```{r, fig.width=8.5}
plot_frq(tmp$q21, type='histogram', geom.size = 1, xlim = c(1,20), ylim=c(0,18), show.prc = FALSE, show.n = FALSE, 
         show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
    geom_boxplot(data=tmp, aes(x=q21, y=15), alpha=0.8, width=2.5, fill="#587db6") +
    geom_jitter(data=tmp, aes(x=q21, y=15), position=position_jitter(width=1.2, height=1), alpha=0.7) +
  scale_x_continuous(breaks=c(seq(1,40,5), 41), labels=xlbls) + xlab('Weekly Hours')
```
`r fig.cap(page.num, "Weekly Unpaid Hours Distribution")`

*Note that "41+" was rounded for 41 in the following analysis for the unpaid hours worked per week*. 

The average number of unpaid hours worked per week (denoted by the dotted line) is `r round(mean(tmp$q21, na.rm = TRUE), 2)`, while the median is `r median(tmp$q21, na.rm = TRUE)` hours. It seems that the majority of students do not work unpaid positions, with `r names(sort(table(tmp$q21), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$q21), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$q21), decreasing=TRUE)[2])` hours following that.

<br />

### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click arrow for campus breakdown of unpaid weekly hours. </summary>
```{r}
tmp <- tmp2 %>% filter(q21> 0)
```
**`r print_n_reporting_tmp('q21')`**  
*Note: below hours were filtered to only include people that worked (> 0 hours) an unpaid job. The value "41+" was also rounded to 41 for the graph/calculations.*
```{r, fig.height=7, fig.width=7}
ggplot(tmp, aes(x=q21, group=school, fill=school)) + geom_histogram(aes(y=..density..), color="black", position = "identity")  +
  geom_density(alpha=0.4, color="black") + facet_wrap(~school, dir="v", scales='free') + xlab('Weekly Unpaid Hours') + ylab("Density") + 
  theme(legend.position="none", strip.background = element_rect(fill="#c7dcf0"), strip.text = element_text(size=11)) +
  scale_fill_manual(values=campus.colors) + scale_x_continuous(breaks=seq(1,41,5), labels=c(as.character(seq(1,36,5)), "41+"))
```
`r fig.cap(page.num, "Weekly Unpaid Hour Distribution by Campus")`

Looking at the breakdown of both graphs, the distribution of unpaid weekly hours worked for Northridge and Fresno seem to be almost identical while Chico seems to have students who work more unpaid weekly hours. CSU Northridge has a mean value of `r unname(round(tapply(tmp$q21, tmp$school, mean)[3],2))` hours and a median of `r unname(round(tapply(tmp$q21, tmp$school, median)[3],2))` hours.  CSU Fresno has a mean value of `r unname(round(tapply(tmp$q21, tmp$school, mean)[2],2))` hours and a median of `r unname(round(tapply(tmp$q21, tmp$school, median)[2],2))` hours. CSU Chico has a mean value of `r unname(round(tapply(tmp$q21, tmp$school, mean)[1],2))` hours and a median of `r unname(round(tapply(tmp$q21, tmp$school, median)[1],2))` hours.
</details>
<br />

## Unpaid Caregiving Hours
**Estimate the number of hours you spend each week on unpaid family obligations (for example, taking care of younger siblings, preparing family meals, running errands for the family, etc.). `r print_n_reporting('caregiving_hours')`**
```{r}
bns$caregiving_hours <- fct_relevel(factor(bns$caregiving_hours), "0", "1-5", "6-10")

plot_frq(bns$caregiving_hours) + xlab('Unpaid Caregiving Hours Per Week')
```
`r fig.cap(page.num, "Weekly Caregiving Hour Ranges")`

It seems that the majority of people in the data do spend some time each week caring for family members. Only `r unname(table(bns$caregiving_hours)['0'])` people estimated that they spent 0 hours per week for family obligations. There are also around the same number of people who estimated they work full-time (40 or more hours per week) on these family obligations. Below is a breakdown of these unpaid hours spent on family obligations each week.

### Exact Hours Breakdown
```{r}
# filtered data before printing n and %
tmp <- data.frame(q22=bns$q22) %>% mutate(q22=recode(q22, "41+"="41"), q22=as.numeric(q22)) %>%
  filter(q22 > 0)
```
Although some of the participants claim to work 0 hours per week, below is a breakdown of the exact number of hours for those who claim to spend time on unpaid family obligations `r print_n_reporting_tmp("q22")`
```{r, fig.width=8.5}
plot_frq(tmp$q22, type='histogram', geom.size = 1, xlim = c(1,20), show.prc = FALSE, show.n = FALSE, 
         show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
    geom_boxplot(data=tmp, aes(x=q22, y=53), alpha=0.8, width=8, fill="#587db6") +
    geom_jitter(data=tmp, aes(x=q22, y=53), position=position_jitter(width=1.5, height=3), alpha=0.7) +
  scale_x_continuous(breaks=c(seq(1,40,5), 41), labels=xlbls) + xlab('Weekly Hours')
```
`r fig.cap(page.num, "Weekly Caregiving Hours Distribution")`

*Note that "41+" was rounded for 41 in the following analysis for the unpaid caregiving hours worked per week*. 

The average number of unpaid caregiving hours worked per week (denoted by the dotted line) is `r round(mean(tmp$q22, na.rm = TRUE), 2)`, while the median is `r median(tmp$q22, na.rm = TRUE)` hours. There does not seem to be a clear pattern in the number of unpaid caregiving hours worked, with `r names(sort(table(tmp$q22), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$q22), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$q22), decreasing=TRUE)[2])` hours following that (`r unname(sort(table(tmp$q22), decreasing=TRUE)[2])` people). 

## Academic Workload
```{r}
xlbls <- as.character(c(seq(0,63,3), "66+"))
tmp <- tmp2
```
**Below is a breakdown of the academic workload, using the 3 hours of work per unit measurement `r print_n_reporting_tmp("q18")`** *Note that values denoted as "22+" are now "66+", but were rounded to 66 for the analysis below*.
```{r, fig.width=7}
plot_frq(tmp$units, type='histogram', show.prc = FALSE, show.n = FALSE, show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
  geom_boxplot(data=tmp, aes(x=units, y=125), alpha=0.8, width=15, fill="#587db6") +
  geom_jitter(data=tmp, aes(x=units, y=125), position=position_jitter(width=1.5, height=6.8), alpha=0.7) + 
  scale_x_continuous(breaks=seq(0,66,3), labels=xlbls) + xlab('Academic Hours Per Week')
```
`r fig.cap(page.num, "Academic Hours Distribution")`

The average number of academic hours worked per week (denoted by the dotted line) is `r round(mean(tmp$units, na.rm = TRUE), 2)`, while the median is `r median(tmp$units, na.rm = TRUE)` hours. The majority of students do seem to be working 36 or more hours per week, with `r names(sort(table(tmp$units), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$units), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$units), decreasing=TRUE)[2])` hours following that (`r unname(sort(table(tmp$units), decreasing=TRUE)[2])` people). 

<br />

### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click arrow for campus breakdown of academic workload. </summary>
```{r}
tmp <- tmp2 %>% filter(units > 0)
```
**Below is a breakdown of the academic workload using the 3 hours of work per unit measurement `r print_n_reporting_tmp('units')`**  
*Note: below the values corresponding to "22+" were rounded to 22. Values were also filtered so that only people who take classes (> 0 hours per week) were included.*
```{r, fig.height=7, fig.width=7}
ggplot(tmp, aes(x=units, group=school, fill=school)) + geom_histogram(aes(y=..density..), color="black", position = "identity")  +
  geom_density(alpha=0.4, color="black") + facet_wrap(~school, dir="v", scales='free') + xlab('Academic Hours') + ylab("Density") + 
  theme(legend.position="none", strip.background = element_rect(fill="#c7dcf0"), strip.text = element_text(size=11)) +
  scale_fill_manual(values=campus.colors) + scale_x_continuous(breaks=c(seq(9,59,7), 66), labels=c(as.character(seq(9,59,7)), "66+"))
```
`r fig.cap(page.num, "Weekly Academic Workload Distribution by Campus")`

Looking at the academic hours across each campus, it seems that the distribution seems very similar for each. CSU Chico has an average unit workload of `r unname(round(tapply(tmp$units, tmp$school, mean, na.rm=TRUE),2)[1])` units, and a median of `r unname(round(tapply(tmp$units, tmp$school, median, na.rm=TRUE),2)[1])` units. CSU Fresno has an average unit workload of `r unname(round(tapply(tmp$units, tmp$school, mean, na.rm=TRUE),2)[2])` units, and a median of `r unname(round(tapply(tmp$units, tmp$school, median, na.rm=TRUE),2)[2])` units. CSU Northridge has an average unit workload of `r unname(round(tapply(tmp$units, tmp$school, mean, na.rm=TRUE),2)[3])` units, and a median of `r unname(round(tapply(tmp$units, tmp$school, median, na.rm=TRUE),2)[3])` units.
</details>
<br />


## Non-Academic Workload
```{r}
xlbls <- as.character(c(seq(2,77, 5), "82+"))
tmp <- tmp2 %>% filter(NonAcademic > 0 | is.na(NonAcademic))
```
**Below is a combination of both paid and unpaid hours worked by students to get a further understanding of the workload participants face on a weekly basis. The values are also filtered so that only people who worked (more than 0 hours in total) were included `r print_n_reporting_tmp("NonAcademic")`** *Note that values denoted as "41+" were added together to form "82+", but are rounded to 82 for the analysis below*.
```{r, fig.width=8}
plot_frq(tmp$NonAcademic, type='histogram', geom.size=1, xlim=c(2,82), ylim=c(0,55), show.prc = FALSE, 
         show.n = FALSE, show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
  geom_boxplot(data=tmp, aes(x=NonAcademic, y=45), alpha=0.8, width=7, fill="#587db6") +
  geom_jitter(data=tmp, aes(x=NonAcademic, y=45), position=position_jitter(width=1.5, height=3), alpha=0.7) + 
  scale_x_continuous(breaks=seq(2,82, 5), labels=xlbls) + xlab('Total Work Hours Per Week')
```
`r fig.cap(page.num, "Non-Academic Hours Distribution")`

The average number of total hours worked per week (denoted by the dotted line) is `r round(mean(tmp$NonAcademic, na.rm = TRUE), 2)`, while the median is `r median(tmp$NonAcademic, na.rm = TRUE)` hours. The majority of students do seem to be working under 40 hours per week in total, with `r names(sort(table(tmp$NonAcademic), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$NonAcademic), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$NonAcademic), decreasing=TRUE)[2])` hours following that (`r unname(sort(table(tmp$NonAcademic), decreasing=TRUE)[2])` people). 

<br />

### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click arrow for campus breakdown of non-academic workload. </summary>
```{r}
tmp <- tmp2 %>% filter(NonAcademic > 0)
```
**Below is a combination of both paid and unpaid hours worked by students to get a further understanding of the workload participants face on a weekly basis `r print_n_reporting_tmp('NonAcademic')`**  
*Note: below the values corresponding to "41+" were rounded to 41. Values were also filtered so that only people who work (> 0 hours per week) were included.*
```{r, fig.height=7, fig.width=7}
ggplot(tmp, aes(x=NonAcademic, group=school, fill=school)) + geom_histogram(aes(y=..density..), color="black", position = "identity")  +
  geom_density(alpha=0.4, color="black") + facet_wrap(~school, dir="v", scales='free') + xlab('Non-Academic Hours') + ylab("Density") + 
  theme(legend.position="none", strip.background = element_rect(fill="#c7dcf0"), strip.text = element_text(size=11)) +
  scale_fill_manual(values=campus.colors) + scale_x_continuous(breaks=seq(2,82,10), labels=c(as.character(seq(2,72,10)), "82+"))
```
`r fig.cap(page.num, "Weekly Non-Academic Workload Distribution by Campus")`

Looking at the non-academic workload across each campus, it seems the distributions are slightly different for each campus. CSU Chico, who seem to have students who work the most paid/unpaid weekly hours, has an average non-academic workload of `r unname(round(tapply(tmp$NonAcademic, tmp$school, mean, na.rm=TRUE),2)[1])` hours and a median of `r unname(round(tapply(tmp$NonAcademic, tmp$school, median, na.rm=TRUE),2)[1])` hours. CSU Fresno, who seem to have students who work the least paid/unpaid weekly hours, has an average non-academic workload of `r unname(round(tapply(tmp$NonAcademic, tmp$school, mean, na.rm=TRUE),2)[2])` hours and a median of `r unname(round(tapply(tmp$NonAcademic, tmp$school, median, na.rm=TRUE),2)[2])` hours. CSU Northridge, who seem to be between the other two campuses, has an average non-academic workload of `r unname(round(tapply(tmp$NonAcademic, tmp$school, mean, na.rm=TRUE),2)[3])` hours and a median of `r unname(round(tapply(tmp$NonAcademic, tmp$school, median, na.rm=TRUE),2)[3])` hours.
</details>
<br />

## Total Workload
```{r}
tmp <- tmp2 %>% filter(TotalHours > 0)
```
**Below is a combination of all worked hours per week, both academic and non-academic. This includes units (3 hr/unit), paid, and unpaid worked hours `r print_n_reporting_tmp("TotalHours")`** *Note that values denoted as "41+" and "22+" were rounded to 41 and 22 (respectively) for the below analysis*.
```{r, fig.width=8}
plot_frq(tmp$TotalHours, type='histogram', geom.size=1.9, ylim=c(0,55), show.prc = FALSE, 
         show.n = FALSE, show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
  geom_boxplot(data=tmp, aes(x=TotalHours, y=45), alpha=0.8, width=7, fill="#587db6") +
  geom_jitter(data=tmp, aes(x=TotalHours, y=45), position=position_jitter(width=1.5, height=3), alpha=0.7) + 
  scale_x_continuous(breaks=floor(seq(10,135,12.5)), labels=floor(seq(9,134,12.5))) + xlab('Total Hours Per Week')
```
`r fig.cap(page.num, "Total Workload Hours Distribution")`

The average number of total hours worked per week (denoted by the dotted line) is `r round(mean(tmp$TotalHours, na.rm = TRUE), 2)`, while the median is `r median(tmp$TotalHours, na.rm = TRUE)` hours. The majority of students do seem to be working over full-time in total, with `r names(sort(table(tmp$TotalHours), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$TotalHours), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$TotalHours), decreasing=TRUE)[2])` hours following that (`r unname(sort(table(tmp$TotalHours), decreasing=TRUE)[2])` people).

<br />

### `r emoji.1` `r emoji.2` Campus Breakdown
<details>
<summary> Click arrow for campus breakdown of total workload. </summary>
```{r}
tmp <- tmp2 %>% filter(TotalHours > 0 | is.na(TotalHours))
```
**Below is a combination of all worked hours per week, both academic and non-academic. This includes units (3 hr/unit), paid, and unpaid worked hours `r print_n_reporting_tmp('TotalHours')`**    
*Note: below the values corresponding to "41+" were rounded to 41, as well as values corresponding to "22+" being rounded to 22. Values were also filtered so that only people who work (> 0 hours per week) were included.*
```{r, fig.height=7, fig.width=7}
ggplot(tmp, aes(x=TotalHours, group=school, fill=school)) + geom_histogram(aes(y=..density..), color="black", position = "identity")  +
  geom_density(alpha=0.4, color="black") + facet_wrap(~school, dir="v", scales='free') + xlab('Total Hours') + ylab("Density") + 
  theme(legend.position="none", strip.background = element_rect(fill="#c7dcf0"), strip.text = element_text(size=11)) +
  scale_fill_manual(values=campus.colors) + scale_x_continuous(breaks=c(seq(9,134,10), 134), labels=as.character(c(seq(9,134,10), 134)))
```
`r fig.cap(page.num, "Weekly Total Workload Distribution by Campus")`

Looking at the total workload hours across each campus, again it seems that the distribution are very similar for each. CSU Chico has an average total workload of `r unname(round(tapply(tmp$TotalHours, tmp$school, mean, na.rm=TRUE),2)[1])` hours, and a median of `r unname(round(tapply(tmp$TotalHours, tmp$school, median, na.rm=TRUE),2)[1])` hours. CSU Fresno has an average total workload of `r unname(round(tapply(tmp$TotalHours, tmp$school, mean, na.rm=TRUE),2)[2])` hours, and a median of `r unname(round(tapply(tmp$TotalHours, tmp$school, median, na.rm=TRUE),2)[2])` hours. CSU Northridge has an average total workload of `r unname(round(tapply(tmp$TotalHours, tmp$school, mean, na.rm=TRUE),2)[3])` hours, and a median of `r unname(round(tapply(tmp$TotalHours, tmp$school, median, na.rm=TRUE),2)[3])` hours. A small number of students also claim to work over 100 hours per week across academic and non-academic jobs.
</details>
<br />

## CalFresh Workload
People are required to meet a certain work criteria in order to receive CalFresh benefits. All able-bodied adults are required to work a minimum of 80 hours per month, which can be broken down into roughly 20 hours per week. This can be either paid or unpaid work, and more information on this requirement can be found on the  [Department of Social Services](https://www.cdss.ca.gov/inforesources/calfresh/abawd#:~:text=People%20who%20are%20ABAWDs%20must,%2C%20and%20in%2Dkind%20work.) website. If you are an student, you may be enrolled in at least 6 academic units or more (equivalent to 18+ hours per week of academic workload) rather than having a paid/unpaid job. For more information on student eligibility, see the [College Student Eligibility](https://www.csuchico.edu/calfresh/basics/college-student-eligibility.shtml) requirements on Chico State's website. 

The below graphs breaks down if a person meets the workload requirements based solely on one of the following criteria:

- Academic workload - enrolled in 6 or more units (18 or more hours).
- Paid Workload - working 20+ weekly hours at a paid position.
- Unpaid Workload - working 20+ weekly hours at a unpaid position.
- Total Workload - working 20+ weekly hours in total (combination of academic, paid, and unpaid).

*Note: people with a workload of 0 hours were included in the graph and analysis.*
```{r, fig.height=3.4, fig.width=8}
tmp <- tmp2
tmp <- tmp %>% mutate(student=factor(ifelse(is.na(q18), NA, ifelse(q18 >= 18, "Eligible", "Not Eligible")), levels=c("Not Eligible", "Eligible")),
                      paid=factor(ifelse(is.na(q19), NA, ifelse(q19 >= 20, "Eligible", "Not Eligible")), levels=c("Not Eligible", "Eligible")),
                      unpaid=factor(ifelse(is.na(q21), NA, ifelse(q21 >= 20, "Eligible", "Not Eligible")), levels=c("Not Eligible", "Eligible")),
                      total=factor(ifelse(is.na(TotalHours), NA, ifelse(TotalHours >= 20, "Eligible", "Not Eligible")), 
                                   levels=c("Not Eligible", "Eligible"))) %>%
  select(student, paid, unpaid, total)

names(tmp) <- c("Academic Workload", "Paid Workload", "Unpaid Workload", "Total Workload")

plot_likert(tmp,
            grid.range = c(1.2, 1.2),
            wrap.legend.labels = 20,
            expand.grid = FALSE,
            values = "sum.outside",
            catcount = 2,
            geom.colors = c("#D8B365","#5AB4AC"),
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
`r fig.cap(page.num, "CalFresh Workload Qualification Breakdown")`

- Looking at the academic workload, we can see a large majority of them are taking more than 6 units and are meet the eligibility requirements (`r unname(table(tmp['Academic Workload'])['Eligible'])` people). A very small minority of participants are not taking more than 6 units and do not meet the eligibility requirements (`r unname(table(tmp['Academic Workload'])['Not Eligible'])` people).
- Looking at the paid workload, we can see that less than half of them work 20 or more hours per week and meet the eligibility requirements (`r unname(table(tmp['Paid Workload'])['Eligible'])` people). A little over half work less than 20 hours per week and do not meet the eligibility requirements (`r unname(table(tmp['Paid Workload'])['Not Eligible'])` people).
- Looking at the unpaid workload, we can see that only a minority of them work 20 or more hours per week and meet the eligibility requirements (`r unname(table(tmp['Unpaid Workload'])['Eligible'])` people). The vast majority work less than 20 hours per week and do not meet the eligibility requirements (`r unname(table(tmp['Unpaid Workload'])['Not Eligible'])` people).
- Looking at the total workload, we can see that the majority of them work 20 or more hours per week and meet the eligibility requirements (`r unname(table(tmp['Total Workload'])['Eligible'])` people). Only a small number work less than 20 hours per week and do not meet the eligibility requirements (`r unname(table(tmp['Total Workload'])['Not Eligible'])` people).

```{r}
rm(tmp, tmp2) # remove data sets
```



