---
title: "Workload"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
editor_options: 
  chunk_output_type: console
---


```{r, include=FALSE}
source("common_code.R")
```

## Weekly Paid Work Hours
**Estimate the number of hours you work in a PAID job (for example, server at a restaurant, office assistant, etc.) or paid internship (for example, training, shadowing, or practicum) per week.**
```{r}
bns$paid_work_hours <- fct_relevel(factor(bns$paid_work_hours), "0", "1-5", "6-10")

plot_frq(bns$paid_work_hours, ylim=c(0,150)) + xlab('Paid Hours Per Week')
```
It seems that the majority of people work either part-time or not at all. Only a small number of people are considered to be working full-time (40 or more hours per week). Below is a breakdown of the exact paid hours worked by survey participants as well as the impacts that COVID had on their hours. 

### Exact Hours Breakdown
Although the majority of the participants claim to work 0 hours per week, below is a breakdown of the exact number of hours for those who claim to work a paid job:
```{r, fig.width=8.5}
xlbls <- c(as.character(seq(1,40,5)), "41+")

tmp <- data.frame(q19=bns$q19) %>% mutate(q19=recode(q19, "41+"="41"), q19=as.numeric(q19)) %>%
  filter(q19 > 0)

plot_frq(tmp$q19, type='histogram', geom.size = 1, xlim = c(1,20), show.prc = FALSE, show.n = FALSE, 
         show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
    geom_boxplot(data=tmp, aes(x=q19, y=45), alpha=0.8, width=6, fill="#587db6") +
    geom_jitter(data=tmp, aes(x=q19, y=45), position=position_jitter(width=2, height=2.2), alpha=0.7) +
  scale_x_continuous(breaks=c(seq(1,40,5), 41), labels=xlbls) + xlab('Weekly Hours')
```
*Note that "41+" was rounded for 41 in the following analysis for the paid hours worked per week*. 

The average number of paid hours worked per week (denoted by the dotted line) is `r round(mean(tmp$q19, na.rm = TRUE), 2)`, while the median is `r median(tmp$q19, na.rm = TRUE)` hours. It seems that the majority of students are considered part-time workers (less than 40 hours per week), with `r names(sort(table(tmp$q19), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$q29), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$q19), decreasing=TRUE)[2])` hours following that.

### Impact of COVID
**Have the hours you work in a PAID job or internship changed due to COVID-19?**
```{r, fig.width=8}
plot_frq(bns$q20, ylim=c(0,135), wrap.labels = 20, sort.frq = 'desc') + xlab('')
```
With the impact of COVID, it seems that most people were able to keep their current paid jobs with only slight changes. `r unname(table(bns$q20)['Yes, my hours have decreased but I still have a job.'])` people had their hours decrease, `r unname(table(bns$q20)['No, my hours have remained the same.'])` people maintained the same hours, and `r unname(table(bns$q20)['Yes, my hours have increased and I still have a job or I have a new job.'])` people had their hours increase. There was also `r unname(table(bns$q20)['Yes, I no longer have my job/internship.'])` people who claimed that they no longer had their paid position due to the impact of COVID, while `r unname(table(bns$q20)['I did not have a job or internship before COVID-19 and I still do not.'])` people also claimed that they did not have a paid position before COVID.

## Unpaid Work Hours
**Estimate the number of hours you work in an UNPAID internship (for example, training, shadowing, practicum, and/or volunteer, etc.). Do not combine with answers above. **
```{r, fig.height=4.5}
bns$unpaid_work_hours <- fct_relevel(factor(bns$unpaid_work_hours), "0", "1-5", "6-10")

plot_frq(bns$unpaid_work_hours) + xlab('Unpaid Hours Per Week')
```
We can see that the majority of people (`r unname(table(bns$unpaid_work_hours)['0'])`) do not work an unpaid job. A small number of people work part-time at an unpaid job and only a select few people work full-time at an unpaid job. Below is a breakdown of the number of unpaid hours worked per week.

### Exact Hours Breakdown
Although the majority of the participants claim to work 0 hours per week, below is a breakdown of the exact number of hours for those who claim to work a unpaid job:
```{r, fig.width=8.5}
tmp <- data.frame(q21=bns$q21) %>% mutate(q21=recode(q21, "41+"="41"), q21=as.numeric(q21)) %>%
  filter(q21 > 0)

plot_frq(tmp$q21, type='histogram', geom.size = 1, xlim = c(1,20), ylim=c(0,18), show.prc = FALSE, show.n = FALSE, 
         show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
    geom_boxplot(data=tmp, aes(x=q21, y=15), alpha=0.8, width=2.5, fill="#587db6") +
    geom_jitter(data=tmp, aes(x=q21, y=15), position=position_jitter(width=1.2, height=1), alpha=0.7) +
  scale_x_continuous(breaks=c(seq(1,40,5), 41), labels=xlbls) + xlab('Weekly Hours')
```
*Note that "41+" was rounded for 41 in the following analysis for the unpaid hours worked per week*. 

The average number of unpaid hours worked per week (denoted by the dotted line) is `r round(mean(tmp$q21, na.rm = TRUE), 2)`, while the median is `r median(tmp$q21, na.rm = TRUE)` hours. It seems that the majority of students do not work unpaid positions, with `r names(sort(table(tmp$q21), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$q21), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$q21), decreasing=TRUE)[2])` hours following that.

## Unpaid Caregiving Hours
**Estimate the number of hours you spend each week on unpaid family obligations (for example, taking care of younger siblings, preparing family meals, running errands for the family, etc.)**
```{r}
bns$caregiving_hours <- fct_relevel(factor(bns$caregiving_hours), "0", "1-5", "6-10")

plot_frq(bns$caregiving_hours) + xlab('Unpaid Caregiving Hours Per Week')
```
It seems that the majority of people in the data do spend some time each week caring for family members. Only `r unname(table(bns$caregiving_hours)['0'])` people estimated that they spent 0 hours per week for family obligations. There are also around the same number of people who estimated they work full-time (40 or more hours per week) on these family obligations. Below is a breakdown of these unpaid hours spent on family obligations each week.

### Exact Hours Breakdown
Although some of the participants claim to work 0 hours per week, below is a breakdown of the exact number of hours for those who claim to spend time on unpaid family obligations:
```{r, fig.width=8.5}
tmp <- data.frame(q22=bns$q22) %>% mutate(q22=recode(q22, "41+"="41"), q22=as.numeric(q22)) %>%
  filter(q22 > 0)

plot_frq(tmp$q22, type='histogram', geom.size = 1, xlim = c(1,20), show.prc = FALSE, show.n = FALSE, 
         show.mean = TRUE, show.mean.val = FALSE, show.sd = FALSE) +
    geom_boxplot(data=tmp, aes(x=q22, y=53), alpha=0.8, width=8, fill="#587db6") +
    geom_jitter(data=tmp, aes(x=q22, y=53), position=position_jitter(width=1.5, height=3), alpha=0.7) +
  scale_x_continuous(breaks=c(seq(1,40,5), 41), labels=xlbls) + xlab('Weekly Hours')
```
*Note that "41+" was rounded for 41 in the following analysis for the unpaid caregiving hours worked per week*. 

The average number of unpaid caregiving hours worked per week (denoted by the dotted line) is `r round(mean(tmp$q22, na.rm = TRUE), 2)`, while the median is `r median(tmp$q22, na.rm = TRUE)` hours. There does not seem to be a clear pattern in the number of unpaid caregiving hours worked, with `r names(sort(table(tmp$q22), decreasing=TRUE)[1])` hours being most common (`r unname(sort(table(tmp$q22), decreasing=TRUE)[1])` people) and `r names(sort(table(tmp$q22), decreasing=TRUE)[2])` hours following that (`r unname(sort(table(tmp$q22), decreasing=TRUE)[2])` people). 

```{r}
rm(tmp) # remove tmp data set
```





